---
title: "Simulations fitness data"
author: "Laure Olazcuaga, Nicolas Rode"
date: "`r format(Sys.Date(), '%d-%B-%Y')`"
output: 
  html_document:
    theme: "journal"
    toc: true
    toc_depth: 3
    number_sections: true
    toc_float:
      collapsed: false
      smooth_scroll: false
editor_options: 
  chunk_output_type: console
---


```{r setup, include =FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
devtools::load_all()
```

# Colors plot
```{r } 
colors <- c("LMER" = "#DCA237", "Anova" = "#459B76")
lines <- c("Balanced" = "solid", "Unbalanced" = "dotted")
```


# BALANCED DESIGN
# Normal distribution
## Simulation
```{r } 

# Power Analyses
nb_simul <- 10000

#Perform siluations
sim <- sapply(1:nb_simul, simul_fitnessdata, distrib = "normal", design = "balanced",
              rho = -0.05, rho_ng = -0.05, 
              npop_per_fruit = 5, nfruit = 3, nhab = 3, nrep = 10, sdpop = 0.5, 
              sdfruithab = 0.5, sdfruithab_ng = 0.5, sigma = 0.5)
sim <- as.data.frame(t(sim))

#Add indic SA
sim <- add_indic_sign(sim)

#Add number of simul for each SA value to keep only 100 simuls per SA value
sim <- add_sim_number_SA(sim)


## Local adaptation (genetic)
tapply(sim$IndicGen[sim$index_SA_Gen<101], sim$SA_Gen[sim$index_SA_Gen<101], length)
tapply(sim$IndicGen_aov[sim$index_SA_Gen<101], sim$SA_Gen[sim$index_SA_Gen<101], mean)

## Local adaptation (non genetic)
tapply(sim$IndicNonGen[sim$index_SA_NonGen<101], sim$SA_NonGen[sim$index_SA_NonGen<101], mean)
tapply(sim$IndicNonGen_aov[sim$index_SA_NonGen<101], sim$SA_NonGen[sim$index_SA_NonGen<101], mean)

tapply(sim$IndicGen, sim$SA_Gen, length)
tapply(sim$IndicNonGen, sim$SA_NonGen, length)

```



## Plot
```{r } 
####################################
###### Plot genetic
####################################


#Number of simuls for each SA value
tapply(sim$index_SA_Gen, sim$SA_Gen, length)

#Save the same number of simuls for each SA value
nb_per_SA=450
sim_select_genetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")
#To check 
# dim(sim)
# dim(sim_select_genetic)
# tapply(sim_select_genetic$index_SA_Gen, sim_select_genetic$SA_Gen, length)

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_genet = sort(unique(sim_select_genetic$SA_Gen)), 
                 prop_val_sign = tapply(sim_select_genetic$IndicGen, 
                                        sim_select_genetic$SA_Gen, mean), 
                 prop_val_sign_aov = tapply(sim_select_genetic$IndicGen_aov, 
                                        sim_select_genetic$SA_Gen, mean))



#Plot
plot_genetic_normal<-ggplot2::ggplot(data = data_prop, aes(x=val_SA_genet)) + 
   geom_point(aes(y=prop_val_sign, color="LMER"), size = 4) + 
   geom_line(aes(y=prop_val_sign, color="LMER", linetype = "Balanced"), size = 1.5) + 
   geom_point(aes(y=prop_val_sign_aov, color="Anova"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign_aov, color="Anova", linetype = "Balanced"), size = 0.75) + 
   ylab("Proportion of simulations with\nsignificant genetic local adaption")  +
   xlab("Intensity of genetic local adaptation (SA)")  +
   ggtitle("Normal data") +
   theme_LO_sober  + 
   ggtitle("Normal data") +
   labs(color = "Methods", linetype = "Design") +
   scale_color_manual(values = colors) +
   scale_linetype_manual(values = lines)
plot_genetic_normal


# #Save plot
# name_plot<-paste0("Simul_powertest_genetic_normal_",
#       nb_simul,"nbsimul_",nb_per_SA,
#       "nbsimulperSA.pdf")
# cowplot::save_plot(file =here::here("figures",name_plot ),
#                   plot_genetic_normal, base_height = 10/cm(1), base_width = 14/cm(1), dpi = 1200)


################################# 
### Plot non-genetic
#################################
#Number of simuls for each SA non genetic value
tapply(sim$index_SA_NonGen, sim$SA_NonGen, length)

#Save the same number of simuls for each SA value
nb_per_SA 
sim_select_nongenetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "non-genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")
#To check 
# dim(sim)
# dim(sim_select_nongenetic)
# tapply(sim_select_nongenetic$index_SA_Gen, sim_select_nongenetic$SA_Gen, length)
# tapply(sim_select_nongenetic$index_SA_NonGen, sim_select_nongenetic$SA_NonGen, length)

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_nongenet = sort(unique(sim_select_nongenetic$SA_NonGen)), 
                 prop_val_sign = tapply(sim_select_nongenetic$IndicNonGen, 
                                        sim_select_nongenetic$SA_NonGen, mean), 
                 prop_val_sign_aov = tapply(sim_select_nongenetic$IndicNonGen_aov, 
                                        sim_select_nongenetic$SA_NonGen, mean))


colors<-c("LMER" = "#DCA237", "Anova" = "#459B76")
#Plot
plot_nongenetic_normal<-ggplot2::ggplot(data = data_prop, aes(x=val_SA_nongenet)) + 
   geom_point(aes(y=prop_val_sign, color="LMER"), size = 4) + 
   geom_line(aes(y=prop_val_sign, color="LMER", linetype = "Balanced"), size = 1.5) + 
   geom_point(aes(y=prop_val_sign_aov, color="Anova"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign_aov, color="Anova", linetype = "Balanced"), size = 0.75) + 
   ylab("Proportion of simulations with\nsignificant non-genetic local adaption")  +
   xlab("Intensity of non-genetic local adaptation (SA)")  +
   theme_LO_sober + 
   ggtitle("Normal data") +
   labs(color = "Methods", linetype = "Design") +
   scale_color_manual(values = colors) +
   scale_linetype_manual(values = lines)
plot_nongenetic_normal


#Save plot
# name_plot<-paste0("Simul_powertest_nongenetic_normal_",
#       nb_simul,"nbsimul_",nb_per_SA,
#       "nbsimulperSA.pdf")
# cowplot::save_plot(file =here::here("figures",name_plot ),
#                   plot_nongenetic_normal, base_height = 10/cm(1), base_width = 14/cm(1), dpi = 1200)


#################################
### Common plot
#################################

power_plot_normal<-cowplot::plot_grid(plot_nongenetic_normal,plot_genetic_normal,
                          labels=c("A", "B"), 
                          label_size = 15,
                          ncol =1, nrow = 2,
                     #    hjust = 0, vjust = 1,
                          scale = c(1,  1))
power_plot_normal



#Save plot
name_plot<-paste0("Simul_powertest_normal_",
      nb_simul,"nbsimul_",nb_per_SA,
      "nbsimulperSA.pdf")
# cowplot::save_plot(file =here::here("figures",name_plot ),
#                   power_plot_normal, base_height = 20/cm(1), base_width = 14/cm(1), dpi = 1200)



```




## False positive rate analyses
### No genetic and no non genetic effects
```{r } 
nb_simul = 10
sim <- sapply(1:nb_simul, simul_fitnessdata, distrib = "normal", design = "balanced",
              rho=0, rho_ng=0, 
              npop_per_fruit = 5, nfruit = 3, nhab = 3, nrep = 10, sdpop = 0.5, 
              sdfruithab = 0.5, sdfruithab_ng = 0.5, sigma = 0.5)

sim <- as.data.frame(t(sim))
sim <- add_indic_sign(sim)
  
## Local adaptation (genetic)
mean(sim$IndicGen)
mean(sim$IndicGen_aov)

## Local adaptation (non genetic)
mean(sim$IndicNonGen)
mean(sim$IndicNonGen_aov)


```



### Genetic effects and no non-genetic effects
```{r } 
sim <- sapply(1:nb_simul, simul_fitnessdata, distrib = "normal", design = "balanced",
              rho=-0.1, rho_ng=0,  
              npop_per_fruit = 5, nfruit = 3, nhab = 3, nrep = 10, sdpop = 0.5, 
              sdfruithab = 0.5, sdfruithab_ng = 0.5, sigma = 0.5)

sim <- as.data.frame(t(sim))
sim <- add_indic_sign(sim)

## Local adaptation (genetic)
tapply(sim$IndicGen, sim$SA_Gen, length)
tapply(sim$IndicGen_aov, sim$SA_Gen, mean)

## Local adaptation (non genetic)
mean(sim$IndicNonGen)
mean(sim$IndicNonGen_aov)

tapply(sim$IndicNonGen, sim$SA_Gen, mean)
tapply(sim$IndicNonGen_aov, sim$SA_Gen, mean)

tapply(sim$IndicNonGen, sim$SA_NonGen, mean)
tapply(sim$IndicNonGen_aov, sim$SA_NonGen, mean)

```



### Non genetic effects and no genetic effects
```{r } 
sim <- sapply(1:nb_simul, simul_fitnessdata, distrib = "normal",design = "balanced",
              rho=0, rho_ng=-0.1,  
              npop_per_fruit = 5, nfruit = 3, nhab = 3, nrep = 10, sdpop = 0.5, 
              sdfruithab = 0.5, sdfruithab_ng = 0.5, sigma = 0.5)
sim <- as.data.frame(t(sim))
sim <- add_indic_sign(sim)

## Local adaptation (genetic)
mean(sim$IndicGen)
mean(sim$IndicGen_aov)

tapply(sim$IndicGen, sim$SA_Gen, mean)
tapply(sim$IndicGen_aov, sim$SA_Gen, mean)

tapply(sim$IndicGen, sim$SA_NonGen, mean)
tapply(sim$IndicGen_aov, sim$SA_NonGen, mean)

## Local adaptation (non genetic)
tapply(sim$IndicNonGen, sim$SA_NonGen, mean)
tapply(sim$IndicNonGen_aov, sim$SA_NonGen, mean)

```




# Poisson distribution
## Simulation
```{r } 

nb_simul <- 10000

#Perform siluations
sim <- sapply(1:nb_simul, simul_fitnessdata, distrib = "poisson", design = "balanced", 
              rho = -0.05, rho_ng = -0.05, 
              npop_per_fruit = 5, nfruit = 3, nhab = 3, nrep = 10, sdpop = 0.5, 
              sdfruithab = 0.5, sdfruithab_ng = 0.5, sigma = 0.5)
sim <- as.data.frame(t(sim))

#Add indic SA
sim <- add_indic_sign(sim)

#Add number of simul for each SA value to keep only 100 simuls per SA value
sim <- add_sim_number_SA(sim)


## Local adaptation (genetic)
tapply(sim$IndicGen[sim$index_SA_Gen<101], sim$SA_Gen[sim$index_SA_Gen<101], length)
tapply(sim$IndicGen_aov[sim$index_SA_Gen<101], sim$SA_Gen[sim$index_SA_Gen<101], mean)

## Local adaptation (non genetic)
tapply(sim$IndicNonGen[sim$index_SA_NonGen<101], sim$SA_NonGen[sim$index_SA_NonGen<101], mean)
tapply(sim$IndicNonGen_aov[sim$index_SA_NonGen<101], sim$SA_NonGen[sim$index_SA_NonGen<101], mean)

tapply(sim$IndicGen, sim$SA_Gen, length)
tapply(sim$IndicNonGen, sim$SA_NonGen, length)

```



## Plot
```{r } 
####################################
###### Plot genetic
####################################


#Number of simuls for each SA value
tapply(sim$index_SA_Gen, sim$SA_Gen, length)

#Save the same number of simuls for each SA value
nb_per_SA=450
sim_select_genetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")

sim_select_genetic[abs(sim_select_genetic$Fratio_Gen-sim_select_genetic$Fratio_Gen_aov)>=0.1,]

#To check 
dim(sim)
dim(sim_select_genetic)
tapply(sim_select_genetic$index_SA_Gen, sim_select_genetic$SA_Gen, length)

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_genet = sort(unique(sim_select_genetic$SA_Gen)), 
                 prop_val_sign = tapply(sim_select_genetic$IndicGen, 
                                        sim_select_genetic$SA_Gen, mean), 
                 prop_val_sign_aov = tapply(sim_select_genetic$IndicGen_aov, 
                                        sim_select_genetic$SA_Gen, mean))


#Plot
plot_genetic_poisson<-ggplot2::ggplot(data = data_prop, aes(x=val_SA_genet)) + 
   geom_point(aes(y=prop_val_sign, color="LMER"), size = 4) + 
   geom_line(aes(y=prop_val_sign, color="LMER", linetype = "Balanced"), size = 1.5) + 
   geom_point(aes(y=prop_val_sign_aov, color="Anova"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign_aov, color="Anova", linetype = "Balanced"), size = 0.75) + 
   ylab("Proportion of simulations with\nsignificant genetic local adaption")  +
   xlab("Intensity of genetic local adaptation (SA)")  +
   ggtitle("Poisson data") +
   theme_LO_sober  + 
   labs(color = "Methods", linetype = "Design") +
   scale_color_manual(values = colors) +
   scale_linetype_manual(values = lines)
plot_genetic_poisson


# #Save plot
# name_plot<-paste0("Simul_powertest_genetic_poisson_",
#       nb_simul,"nbsimul_",nb_per_SA,
#       "nbsimulperSA.pdf")
# cowplot::save_plot(file =here::here("figures",name_plot ),
#                   plot_genetic_poisson, base_height = 10/cm(1), base_width = 14/cm(1), dpi = 1200)


################################# 
### Plot non-genetic
#################################
#Number of simuls for each SA non genetic value
tapply(sim$index_SA_NonGen, sim$SA_NonGen, length)

#Save the same number of simuls for each SA value
nb_per_SA 
sim_select_nongenetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "non-genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")
#To check 
# dim(sim)
# dim(sim_select_nongenetic)
# tapply(sim_select_nongenetic$index_SA_Gen, sim_select_nongenetic$SA_Gen, length)
# tapply(sim_select_nongenetic$index_SA_NonGen, sim_select_nongenetic$SA_NonGen, length)

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_nongenet = sort(unique(sim_select_nongenetic$SA_NonGen)), 
                 prop_val_sign = tapply(sim_select_nongenetic$IndicNonGen, 
                                        sim_select_nongenetic$SA_NonGen, mean), 
                 prop_val_sign_aov = tapply(sim_select_nongenetic$IndicNonGen_aov, 
                                        sim_select_nongenetic$SA_NonGen, mean))


colors<-c("LMER" = "#DCA237", "Anova" = "#459B76")
#Plot
plot_nongenetic_poisson<-ggplot2::ggplot(data = data_prop, aes(x=val_SA_nongenet)) + 
   geom_point(aes(y=prop_val_sign, color="LMER"), size = 4) + 
   geom_line(aes(y=prop_val_sign, color="LMER", linetype = "Balanced"), size = 1.5) + 
   geom_point(aes(y=prop_val_sign_aov, color="Anova"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign_aov, color="Anova", linetype = "Balanced"), size = 0.75) + 
   ylab("Proportion of simulations with\nsignificant non-genetic local adaption")  +
   xlab("Intensity of non-genetic local adaptation (SA)")  +
   ggtitle("Poisson data") +
   theme_LO_sober +
   labs(color = "Methods", linetype = "Design") +
   scale_color_manual(values = colors) +
   scale_linetype_manual(values = lines)
plot_nongenetic_poisson


#Save plot
# name_plot<-paste0("Simul_powertest_nongenetic_poisson_",
#       nb_simul,"nbsimul_",nb_per_SA,
#       "nbsimulperSA.pdf")
# cowplot::save_plot(file =here::here("figures",name_plot ),
#                   plot_nongenetic_poisson, base_height = 10/cm(1), base_width = 14/cm(1), dpi = 1200)


#################################
### Common plot
#################################

power_plot_poisson<-cowplot::plot_grid(plot_nongenetic_poisson,plot_genetic_poisson,
                          labels=c("A", "B"), 
                          label_size = 15,
                          ncol =1, nrow = 2,
                     #    hjust = 0, vjust = 1,
                          scale = c(1,  1))
power_plot_poisson



#Save plot
# name_plot<-paste0("Simul_powertest_poissondata_",
#       nb_simul,"nbsimul_",nb_per_SA,
#       "nbsimulperSA.pdf")
# cowplot::save_plot(file =here::here("figures",name_plot ),
#                   power_plot_poisson, base_height = 20/cm(1), base_width = 14/cm(1), dpi = 1200)
# 
# 

```




## False positive rate analyses
### No genetic and no non genetic effects
```{r } 
nb_simul = 10
sim <- sapply(1:nb_simul, simul_fitnessdata, distrib = "poisson", design = "balanced",
              rho=0, rho_ng=0,  
              npop_per_fruit = 5, nfruit = 3, nhab = 3, nrep = 10, sdpop = 0.5, 
              sdfruithab = 0.5, sdfruithab_ng = 0.5, sigma = 0.5)

sim <- as.data.frame(t(sim))
sim <- add_indic_sign(sim)
  
## Local adaptation (genetic)
mean(sim$IndicGen)
mean(sim$IndicGen_aov)

## Local adaptation (non genetic)
mean(sim$IndicNonGen)
mean(sim$IndicNonGen_aov)

```



### Genetic effects and no non-genetic effects
```{r } 
sim <- sapply(1:nb_simul, simul_fitnessdata, distrib = "poisson", design = "balanced",
              rho=-0.1, rho_ng=0,  
              npop_per_fruit = 5, nfruit = 3, nhab = 3, nrep = 10, sdpop = 0.5, 
              sdfruithab = 0.5, sdfruithab_ng = 0.5, sigma = 0.5)

sim <- as.data.frame(t(sim))
sim <- add_indic_sign(sim)

## Local adaptation (genetic)
tapply(sim$IndicGen, sim$SA_Gen, mean)
tapply(sim$IndicGen_aov, sim$SA_Gen, mean)

## Local adaptation (non genetic)
mean(sim$IndicNonGen)
mean(sim$IndicNonGen_aov)


```



### Non genetic effects and no genetic effects
```{r } 
sim <- sapply(1:nb_simul, simul_fitnessdata, distrib = "poisson",design = "balanced",
              rho=0, rho_ng=-0.1, 
              npop_per_fruit = 5, nfruit = 3, nhab = 3, nrep = 10, sdpop = 0.5, 
              sdfruithab = 0.5, sdfruithab_ng = 0.5, sigma = 0.5)

sim <- as.data.frame(t(sim))
sim <- add_indic_sign(sim)

## Local adaptation (genetic)
mean(sim$IndicGen)
mean(sim$IndicGen_aov)

## Local adaptation (non genetic)
tapply(sim$IndicNonGen, sim$SA_NonGen, mean)
tapply(sim$IndicNonGen_aov, sim$SA_NonGen, mean)

```



# Binomial distribution
## Simulation
```{r } 

nb_simul <- 10000

#Perform siluations
sim <- sapply(1:nb_simul, simul_fitnessdata, distrib = "binomial",design = "balanced",
              rho = -0.05, 
              rho_ng = -0.05, 
              npop_per_fruit = 5, nfruit = 3, nhab = 3, nrep = 10, sdpop = 0.5, 
              sdfruithab = 0.5, sdfruithab_ng = 0.5, sigma = 0.5, ntrial = 60)
sim <- as.data.frame(t(sim))


#Add indic SA
sim <- add_indic_sign(sim)

#Add number of simul for each SA value to keep only 100 simuls per SA value
sim <- add_sim_number_SA(sim)


## Local adaptation (genetic)
tapply(sim$IndicGen[sim$index_SA_Gen<101], sim$SA_Gen[sim$index_SA_Gen<101], length)
tapply(sim$IndicGen_aov[sim$index_SA_Gen<101], sim$SA_Gen[sim$index_SA_Gen<101], mean)

## Local adaptation (non genetic)
tapply(sim$IndicNonGen[sim$index_SA_NonGen<101], sim$SA_NonGen[sim$index_SA_NonGen<101], mean)
tapply(sim$IndicNonGen_aov[sim$index_SA_NonGen<101], sim$SA_NonGen[sim$index_SA_NonGen<101], mean)

tapply(sim$IndicGen, sim$SA_Gen, length)
tapply(sim$IndicNonGen, sim$SA_NonGen, length)

```



## Plot
```{r } 
####################################
###### Plot genetic
####################################


#Number of simuls for each SA value
tapply(sim$index_SA_Gen, sim$SA_Gen, length)

#Save the same number of simuls for each SA value
nb_per_SA=450
sim_select_genetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")
#To check 
# dim(sim)
# dim(sim_select_genetic)
# tapply(sim_select_genetic$index_SA_Gen, sim_select_genetic$SA_Gen, length)

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_genet = sort(unique(sim_select_genetic$SA_Gen)), 
                 prop_val_sign = tapply(sim_select_genetic$IndicGen, 
                                        sim_select_genetic$SA_Gen, mean), 
                 prop_val_sign_aov = tapply(sim_select_genetic$IndicGen_aov, 
                                        sim_select_genetic$SA_Gen, mean))


#Plot
plot_genetic_binomial<-ggplot2::ggplot(data = data_prop, aes(x=val_SA_genet)) + 
   geom_point(aes(y=prop_val_sign, color="LMER"), size = 4) + 
   geom_line(aes(y=prop_val_sign, color="LMER", linetype = "Balanced"), size = 1.5) + 
   geom_point(aes(y=prop_val_sign_aov, color="Anova"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign_aov, color="Anova", linetype = "Balanced"), size = 0.75) + 
   ylab("Proportion of simulations with\nsignificant genetic local adaption")  +
   xlab("Intensity of genetic local adaptation (SA)")  +
   ggtitle("Binomial data") +
   theme_LO_sober +
   labs(color = "Methods", linetype = "Design") +
   scale_color_manual(values = colors) +
   scale_linetype_manual(values = lines)
plot_genetic_binomial


# #Save plot
# name_plot<-paste0("Simul_powertest_genetic_binomial_",
#       nb_simul,"nbsimul_",nb_per_SA,
#       "nbsimulperSA.pdf")
# cowplot::save_plot(file =here::here("figures",name_plot ),
#                   plot_genetic_binomial, base_height = 10/cm(1), base_width = 14/cm(1), dpi = 1200)


################################# 
### Plot non-genetic
#################################
#Number of simuls for each SA non genetic value
tapply(sim$index_SA_NonGen, sim$SA_NonGen, length)

#Save the same number of simuls for each SA value
nb_per_SA 
sim_select_nongenetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "non-genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")
#To check 
# dim(sim)
# dim(sim_select_nongenetic)
# tapply(sim_select_nongenetic$index_SA_Gen, sim_select_nongenetic$SA_Gen, length)
# tapply(sim_select_nongenetic$index_SA_NonGen, sim_select_nongenetic$SA_NonGen, length)

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_nongenet = sort(unique(sim_select_nongenetic$SA_NonGen)), 
                 prop_val_sign = tapply(sim_select_nongenetic$IndicNonGen, 
                                        sim_select_nongenetic$SA_NonGen, mean), 
                 prop_val_sign_aov = tapply(sim_select_nongenetic$IndicNonGen_aov, 
                                        sim_select_nongenetic$SA_NonGen, mean))


colors<-c("LMER" = "#DCA237", "Anova" = "#459B76")
#Plot
plot_nongenetic_binomial<-ggplot2::ggplot(data = data_prop, aes(x=val_SA_nongenet)) + 
   geom_point(aes(y=prop_val_sign, color="LMER"), size = 4) + 
   geom_line(aes(y=prop_val_sign, color="LMER", linetype = "Balanced"), size = 1.5) + 
   geom_point(aes(y=prop_val_sign_aov, color="Anova"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign_aov, color="Anova", linetype = "Balanced"), size = 0.75) + 
   ylab("Proportion of simulations with\nsignificant non-genetic local adaption")  +
   xlab("Intensity of non-genetic local adaptation (SA)")  +
   ggtitle("Binomial data") +
   theme_LO_sober +
   labs(color = "Methods", linetype = "Design") +
   scale_color_manual(values = colors) +
   scale_linetype_manual(values = lines)
plot_nongenetic_binomial


#Save plot
# name_plot<-paste0("Simul_powertest_nongenetic_binomial_",
#       nb_simul,"nbsimul_",nb_per_SA,
#       "nbsimulperSA.pdf")
# cowplot::save_plot(file =here::here("figures",name_plot ),
#                   plot_nongenetic_binomial, base_height = 10/cm(1), base_width = 14/cm(1), dpi = 1200)


#################################
### Common plot
#################################

power_plot_binomial<-cowplot::plot_grid(plot_nongenetic_binomial,plot_genetic_binomial,
                          labels=c("A", "B"), 
                          label_size = 15,
                          ncol =1, nrow = 2,
                     #    hjust = 0, vjust = 1,
                          scale = c(1,  1))
power_plot_binomial



#Save plot
# name_plot<-paste0("Simul_powertest_binomialdata_",
#       nb_simul,"nbsimul_",nb_per_SA,
#       "nbsimulperSA.pdf")
# cowplot::save_plot(file =here::here("figures",name_plot ),
#                   power_plot_binomial, base_height = 20/cm(1), base_width = 14/cm(1), dpi = 1200)
# 
# 


```

## All plots
```{r } 
power_plot_all<-cowplot::plot_grid(plot_nongenetic_normal,plot_nongenetic_poisson,plot_nongenetic_binomial,
                                   plot_genetic_normal, plot_genetic_poisson,plot_genetic_binomial,
                          #labels=c("A", "B"), 
                          #label_size = 15,
                          ncol =3, nrow = 2,
                     #    hjust = 0, vjust = 1,
                          scale = c(1,  1))
power_plot_all



#Save plot
name_plot<-paste0("Simul_powertest_ALLDATA_",
      nb_simul,"nbsimul_",nb_per_SA,
      "nbsimulperSA.pdf")
# cowplot::save_plot(file =here::here("figures",name_plot ),
#                   power_plot_all, base_height = 20/cm(1), base_width = 42/cm(1), dpi = 1200)
# 

```

## False positive rate analyses
### No genetic and no non genetic effects
```{r } 
nb_simul = 10
sim <- sapply(1:nb_simul, simul_fitnessdata, distrib = "binomial", design = "balanced",
              rho=0, rho_ng=0, 
              npop_per_fruit = 5, nfruit = 3, nhab = 3, nrep = 10, sdpop = 0.5, 
              sdfruithab = 0.5, sdfruithab_ng = 0.5, sigma = 0.5)
sim <- as.data.frame(t(sim))
sim <- add_indic_sign(sim)
  
## Local adaptation (genetic)
mean(sim$IndicGen)
mean(sim$IndicGen_aov)

## Local adaptation (non genetic)
mean(sim$IndicNonGen)
mean(sim$IndicNonGen_aov)


```



### Genetic effects and no non-genetic effects
```{r } 
sim <- sapply(1:nb_simul, simul_fitnessdata, distrib = "binomial", design = "balanced",
              rho=-0.1, rho_ng=0,
              npop_per_fruit = 5, nfruit = 3, nhab = 3, nrep = 10, sdpop = 0.5, 
              sdfruithab = 0.5, sdfruithab_ng = 0.5, sigma = 0.5)
sim <- as.data.frame(t(sim))
sim <- add_indic_sign(sim)

## Local adaptation (genetic)
tapply(sim$IndicGen, sim$SA_Gen, mean)
tapply(sim$IndicGen_aov, sim$SA_Gen, mean)

## Local adaptation (non genetic)
mean(sim$IndicNonGen)
mean(sim$IndicNonGen_aov)

```



### Non genetic effects and no genetic effects
```{r } 
### 
sim <- sapply(1:nb_simul, simul_fitnessdata, distrib = "binomial", design = "balanced",
              rho=0, rho_ng=-0.1,
              npop_per_fruit = 5, nfruit = 3, nhab = 3, nrep = 10, sdpop = 0.5, 
              sdfruithab = 0.5, sdfruithab_ng = 0.5, sigma = 0.5)
sim <- as.data.frame(t(sim))
sim <- add_indic_sign(sim)

## Local adaptation (genetic)
mean(sim$IndicGen)
mean(sim$IndicGen_aov)

## Local adaptation (non genetic)
tapply(sim$IndicNonGen, sim$SA_NonGen, mean)
tapply(sim$IndicNonGen_aov, sim$SA_NonGen, mean)

```



# UNBALANCED DESIGN
# Normal distribution
## Simulation
```{r } 
#Simul data 
nb_simul <- 10000
sim <- sapply(1:nb_simul, simul_fitnessdata, distrib = "normal",  design = "unbalanced",
              rho = -0.05, rho_ng = -0.05, 
              npop_per_fruit = 5, nfruit = 3, nhab = 3, nrep = 10, sdpop = 0.5, 
              sdfruithab = 0.5, sdfruithab_ng = 0.5, sigma = 0.5)


sim <- as.data.frame(t(sim))
sim <- add_indic_sign(sim)
sim <- add_sim_number_SA(sim)
```




## Plot
```{r } 
####################################
###### Plot genetic
####################################
#Number of simuls for each SA value
tapply(sim$index_SA_Gen, sim$SA_Gen, length)

#Save the same number of simuls for each SA value
nb_per_SA=450
sim_select_genetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_genet = sort(unique(sim_select_genetic$SA_Gen)), 
                 prop_val_sign = tapply(sim_select_genetic$IndicGen, 
                                        sim_select_genetic$SA_Gen, mean), 
                 prop_val_sign_aov = tapply(sim_select_genetic$IndicGen_aov, 
                                        sim_select_genetic$SA_Gen, mean))


#Plot
plot_genetic_normal_unbalanced<-ggplot2::ggplot(data = data_prop, aes(x=val_SA_genet)) + 
   geom_point(aes(y=prop_val_sign, color="LMER"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign, color="LMER"), size = 1, linetype = "dotted") + 
   geom_point(aes(y=prop_val_sign_aov, color="Anova"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign_aov, color="Anova"), size = 1, linetype = "dotted") + 
   ylab("Proportion of simulations with\nsignificant genetic local adaption")  +
   xlab("Intensity of genetic local adaptation (SA)")  +
   ggtitle("Normal data (unbalanced experimental design)") +
   theme_LO_sober +
   labs(color = "Methods", linetype = "Design") +
   scale_color_manual(values = colors) +
   scale_linetype_manual(values = lines)
plot_genetic_normal_unbalanced


# Balanced + unbabacaled
plot_genetic_normal_ALL <- plot_genetic_normal +
   geom_point(data = data_prop, 
              aes(y=prop_val_sign, x=val_SA_genet, color="LMER"), size = 2.5) + 
   geom_line(data = data_prop, 
             aes(y=prop_val_sign, x=val_SA_genet, 
                 color="LMER", linetype = "Unbalanced"), size = 1) + 
   geom_point(data = data_prop,
              aes(y=prop_val_sign_aov, x=val_SA_genet, 
                  color="Anova"), size = 2.5) + 
   geom_line(data = data_prop, 
             aes(y=prop_val_sign_aov, color="Anova", x=val_SA_genet, 
                 linetype = "Unbalanced"), size = 1) +
   labs(color = "Methods", linetype = "Design") +
   scale_linetype_manual(values = lines)
plot_genetic_normal_ALL


################################# 
### Plot non-genetic
#################################
#Number of simuls for each SA non genetic value
tapply(sim$index_SA_NonGen, sim$SA_NonGen, length)

#Save the same number of simuls for each SA value
nb_per_SA 
sim_select_nongenetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "non-genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_nongenet = sort(unique(sim_select_nongenetic$SA_NonGen)), 
                 prop_val_sign = tapply(sim_select_nongenetic$IndicNonGen, 
                                        sim_select_nongenetic$SA_NonGen, mean), 
                 prop_val_sign_aov = tapply(sim_select_nongenetic$IndicNonGen_aov, 
                                        sim_select_nongenetic$SA_NonGen, mean))


#Plot
plot_nongenetic_normal_unbalanced<-ggplot2::ggplot(data = data_prop, 
                                                   aes(x=val_SA_nongenet)) + 
   geom_point(aes(y=prop_val_sign, color="LMER"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign, color="LMER"), size = 1, linetype = "dotted") + 
   geom_point(aes(y=prop_val_sign_aov, color="Anova"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign_aov, color="Anova"), size = 1, linetype = "dotted") + 
   ylab("Proportion of simulations with\nsignificant non-genetic local adaption")  +
   xlab("Intensity of non-genetic local adaptation (SA)")  +
   theme_LO_sober + 
   ggtitle("Normal data (unbalanced experimental design)") +
   labs(color = "Methods") +
   scale_color_manual(values = colors)
plot_nongenetic_normal_unbalanced




plot_nongenetic_normal_ALL <- plot_genetic_normal +
   geom_point(data = data_prop, 
              aes(y=prop_val_sign, x=val_SA_nongenet, color="LMER"), size = 2.5) + 
   geom_line(data = data_prop, 
             aes(y=prop_val_sign, x=val_SA_nongenet, 
                 color="LMER", linetype = "Unbalanced"), size = 1) + 
   geom_point(data = data_prop,
              aes(y=prop_val_sign_aov, x=val_SA_nongenet, 
                  color="Anova"), size = 2.5) + 
   geom_line(data = data_prop, 
             aes(y=prop_val_sign_aov, color="Anova", x=val_SA_nongenet, 
                 linetype = "Unbalanced"), size = 1) +
   labs(color = "Methods", linetype = "Design") +
   scale_linetype_manual(values = lines)
plot_nongenetic_normal_ALL


```




# Poisson distribution
## Simulation
```{r } 
#Simul data 
#nb_simul <- 1000
sim <- sapply(1:nb_simul, simul_fitnessdata, distrib = "poisson",  design = "unbalanced",
              rho = -0.05, rho_ng = -0.05, 
              npop_per_fruit = 5, nfruit = 3, nhab = 3, nrep = 10, sdpop = 0.5, 
              sdfruithab = 0.5, sdfruithab_ng = 0.5, sigma = 0.5)


sim <- as.data.frame(t(sim))
sim <- add_indic_sign(sim)
sim <- add_sim_number_SA(sim)
```




## Plot
```{r } 
####################################
###### Plot genetic
####################################
#Number of simuls for each SA value
tapply(sim$index_SA_Gen, sim$SA_Gen, length)

#Save the same number of simuls for each SA value
nb_per_SA=450
sim_select_genetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_genet = sort(unique(sim_select_genetic$SA_Gen)), 
                 prop_val_sign = tapply(sim_select_genetic$IndicGen, 
                                        sim_select_genetic$SA_Gen, mean), 
                 prop_val_sign_aov = tapply(sim_select_genetic$IndicGen_aov, 
                                        sim_select_genetic$SA_Gen, mean))


#Plot
plot_genetic_poisson_unbalanced<-ggplot2::ggplot(data = data_prop, aes(x=val_SA_genet)) + 
   geom_point(aes(y=prop_val_sign, color="LMER"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign, color="LMER"), size = 1, linetype = "dotted") + 
   geom_point(aes(y=prop_val_sign_aov, color="Anova"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign_aov, color="Anova"), size = 1, linetype = "dotted") + 
   ylab("Proportion of simulations with\nsignificant genetic local adaption")  +
   xlab("Intensity of genetic local adaptation (SA)")  +
   ggtitle("Poisson data (unbalanced experimental design)") +
   theme_LO_sober  + 
   labs(color = "Methods") +
   scale_color_manual(values = colors)
plot_genetic_poisson_unbalanced




plot_genetic_poisson_ALL <- plot_genetic_poisson +
   geom_point(data = data_prop, 
              aes(y=prop_val_sign, x=val_SA_genet, color="LMER"), size = 2.5) + 
   geom_line(data = data_prop, 
             aes(y=prop_val_sign, x=val_SA_genet, 
                 color="LMER", linetype = "Unbalanced"), size = 1) + 
   geom_point(data = data_prop,
              aes(y=prop_val_sign_aov, x=val_SA_genet, 
                  color="Anova"), size = 2.5) + 
   geom_line(data = data_prop, 
             aes(y=prop_val_sign_aov, color="Anova", x=val_SA_genet, 
                 linetype = "Unbalanced"), size = 1) +
   labs(color = "Methods", linetype = "Design") +
   scale_linetype_manual(values = lines)
plot_genetic_poisson_ALL


################################# 
### Plot non-genetic
#################################
#Number of simuls for each SA non genetic value
tapply(sim$index_SA_NonGen, sim$SA_NonGen, length)

#Save the same number of simuls for each SA value
nb_per_SA 
sim_select_nongenetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "non-genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_nongenet = sort(unique(sim_select_nongenetic$SA_NonGen)), 
                 prop_val_sign = tapply(sim_select_nongenetic$IndicNonGen, 
                                        sim_select_nongenetic$SA_NonGen, mean), 
                 prop_val_sign_aov = tapply(sim_select_nongenetic$IndicNonGen_aov, 
                                        sim_select_nongenetic$SA_NonGen, mean))


colors<-c("LMER" = "#DCA237", "Anova" = "#459B76")
#Plot
plot_nongenetic_poisson_unbalanced<-ggplot2::ggplot(data = data_prop, 
                                                   aes(x=val_SA_nongenet)) + 
   geom_point(aes(y=prop_val_sign, color="LMER"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign, color="LMER"), size = 1, linetype = "dotted") + 
   geom_point(aes(y=prop_val_sign_aov, color="Anova"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign_aov, color="Anova"), size = 1, linetype = "dotted") + 
   ylab("Proportion of simulations with\nsignificant non-genetic local adaption")  +
   xlab("Intensity of non-genetic local adaptation (SA)")  +
   theme_LO_sober + 
   ggtitle("Poisson data (unbalanced experimental design)") +
   labs(color = "Methods") +
   scale_color_manual(values = colors)
plot_nongenetic_poisson_unbalanced




plot_nongenetic_poisson_ALL <- plot_nongenetic_poisson +
   geom_point(data = data_prop, 
              aes(y=prop_val_sign, x=val_SA_nongenet, color="LMER"), size = 2.5) + 
   geom_line(data = data_prop, 
             aes(y=prop_val_sign, x=val_SA_nongenet, 
                 color="LMER", linetype = "Unbalanced"), size = 1) + 
   geom_point(data = data_prop,
              aes(y=prop_val_sign_aov, x=val_SA_nongenet, 
                  color="Anova"), size = 2.5) + 
   geom_line(data = data_prop, 
             aes(y=prop_val_sign_aov, color="Anova", x=val_SA_nongenet, 
                 linetype = "Unbalanced"), size = 1) +
   labs(color = "Methods", linetype = "Design") +
   scale_linetype_manual(values = lines)
plot_nongenetic_poisson_ALL
```






# Binomial distribution
## Simulation
```{r } 
#Simul data 
#nb_simul <- 1000
sim <- sapply(1:nb_simul, simul_fitnessdata, distrib = "binomial",  design = "unbalanced",
              rho = -0.05, rho_ng = -0.05, 
              npop_per_fruit = 5, nfruit = 3, nhab = 3, nrep = 10, sdpop = 0.5, 
              sdfruithab = 0.5, sdfruithab_ng = 0.5, sigma = 0.5, ntrial = 60)

sim <- as.data.frame(t(sim))
sim <- add_indic_sign(sim)
sim <- add_sim_number_SA(sim)
```




## Plot
```{r } 
####################################
###### Plot genetic
####################################
#Number of simuls for each SA value
tapply(sim$index_SA_Gen, sim$SA_Gen, length)

#Save the same number of simuls for each SA value
nb_per_SA=450
sim_select_genetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_genet = sort(unique(sim_select_genetic$SA_Gen)), 
                 prop_val_sign = tapply(sim_select_genetic$IndicGen, 
                                        sim_select_genetic$SA_Gen, mean), 
                 prop_val_sign_aov = tapply(sim_select_genetic$IndicGen_aov, 
                                        sim_select_genetic$SA_Gen, mean))


#Plot
plot_genetic_Binomial_unbalanced<-ggplot2::ggplot(data = data_prop, 
                                                  aes(x=val_SA_genet)) + 
   geom_point(aes(y=prop_val_sign, color="LMER"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign, color="LMER"), size = 1, linetype = "dotted") + 
   geom_point(aes(y=prop_val_sign_aov, color="Anova"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign_aov, color="Anova"), size = 1, linetype = "dotted") + 
   ylab("Proportion of simulations with\nsignificant genetic local adaption")  +
   xlab("Intensity of genetic local adaptation (SA)")  +
   ggtitle("Binomial data (unbalanced experimental design)") +
   theme_LO_sober  + 
   labs(color = "Methods") +
   scale_color_manual(values = colors) 
plot_genetic_Binomial_unbalanced




plot_genetic_binomial_ALL <- plot_genetic_binomial +
   geom_point(data = data_prop, 
              aes(y=prop_val_sign, x=val_SA_genet, color="LMER"), size = 2.5) + 
   geom_line(data = data_prop, 
             aes(y=prop_val_sign, x=val_SA_genet, 
                 color="LMER", linetype = "Unbalanced"), size = 1) + 
   geom_point(data = data_prop,
              aes(y=prop_val_sign_aov, x=val_SA_genet, 
                  color="Anova"), size = 2.5) + 
   geom_line(data = data_prop, 
             aes(y=prop_val_sign_aov, color="Anova", x=val_SA_genet, 
                 linetype = "Unbalanced"), size = 1) +
   labs(color = "Methods", linetype = "Design") +
   scale_linetype_manual(values = lines)
plot_genetic_binomial_ALL

################################# 
### Plot non-genetic
#################################
#Number of simuls for each SA non genetic value
tapply(sim$index_SA_NonGen, sim$SA_NonGen, length)

#Save the same number of simuls for each SA value
nb_per_SA 
sim_select_nongenetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "non-genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_nongenet = sort(unique(sim_select_nongenetic$SA_NonGen)), 
                 prop_val_sign = tapply(sim_select_nongenetic$IndicNonGen, 
                                        sim_select_nongenetic$SA_NonGen, mean), 
                 prop_val_sign_aov = tapply(sim_select_nongenetic$IndicNonGen_aov, 
                                        sim_select_nongenetic$SA_NonGen, mean))


colors<-c("LMER" = "#DCA237", "Anova" = "#459B76")
#Plot
plot_nongenetic_Binomial_unbalanced<-ggplot2::ggplot(data = data_prop, 
                                                   aes(x=val_SA_nongenet)) + 
   geom_point(aes(y=prop_val_sign, color="LMER"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign, color="LMER"), size = 1, linetype = "dotted") + 
   geom_point(aes(y=prop_val_sign_aov, color="Anova"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign_aov, color="Anova"), size = 1, linetype = "dotted") + 
   ylab("Proportion of simulations with\nsignificant non-genetic local adaption")  +
   xlab("Intensity of non-genetic local adaptation (SA)")  +
   theme_LO_sober + 
   ggtitle("Binomial data (unbalanced experimental design)") +
   labs(color = "Methods") +
   scale_color_manual(values = colors)
plot_nongenetic_Binomial_unbalanced



plot_nongenetic_binomial_ALL <- plot_nongenetic_binomial +
   geom_point(data = data_prop, 
              aes(y=prop_val_sign, x=val_SA_nongenet, color="LMER"), 
              size = 2.5) + 
   geom_line(data = data_prop, 
             aes(y=prop_val_sign, x=val_SA_nongenet, 
                 color="LMER", linetype = "Unbalanced"), size = 1) + 
   geom_point(data = data_prop,
              aes(y=prop_val_sign_aov, x=val_SA_nongenet, 
                  color="Anova"), size = 2.5) + 
   geom_line(data = data_prop, 
             aes(y=prop_val_sign_aov, color="Anova", x=val_SA_nongenet, 
                 linetype = "Unbalanced"), size = 1) +
   labs(color = "Methods", linetype = "Design") +
   scale_linetype_manual(values = lines)
plot_nongenetic_binomial_ALL


```



# All plots unbalanced
```{r } 
power_plot_all_unbalanced<-cowplot::plot_grid(plot_nongenetic_normal_unbalanced,
                                   plot_nongenetic_poisson_unbalanced,
                                   plot_nongenetic_Binomial_unbalanced,
                                   plot_genetic_normal_unbalanced,
                                   plot_genetic_poisson_unbalanced,
                                   plot_genetic_Binomial_unbalanced,
                          #labels=c("A", "B"), 
                          #label_size = 15,
                          ncol =3, nrow = 2,
                     #    hjust = 0, vjust = 1,
                          scale = c(1,  1))
power_plot_all_unbalanced



#Save plot
name_plot<-paste0("Simul_powertest_ALLDATA_UNBALANCED",
      nb_simul,"nbsimul_",nb_per_SA,
      "nbsimulperSA.pdf")
# cowplot::save_plot(file =here::here("figures",name_plot ),
#                   power_plot_all_unbalanced, base_height = 20/cm(1),
#                   base_width = 42/cm(1), dpi = 1200)
# 

```






# PLOT Balanced & Unbalanced
```{r } 
POWER_ALL<-cowplot::plot_grid(plot_nongenetic_normal,
                                          plot_nongenetic_poisson,
                                          plot_nongenetic_binomial,
                                          plot_genetic_normal,
                                   plot_genetic_poisson,
                                   plot_genetic_binomial,
                                   plot_nongenetic_normal_unbalanced,
                                   plot_nongenetic_poisson_unbalanced,
                                   plot_nongenetic_Binomial_unbalanced,
                                   plot_genetic_normal_unbalanced,
                                   plot_genetic_poisson_unbalanced,
                                   plot_genetic_Binomial_unbalanced,
                          #labels=c("A", "B"), 
                          #label_size = 15,
                          ncol =3, nrow = 4,
                     #    hjust = 0, vjust = 1,
                          scale = c(1,  1))
POWER_ALL



#Save plot
name_plot<-paste0("Simul_powertest_ALLDATA_BALANCED_and_UNBALANCED",
      nb_simul,"nbsimul_",nb_per_SA,
      "nbsimulperSA.pdf")
cowplot::save_plot(file =here::here("figures",name_plot ),
                  POWER_ALL, base_height = 40/cm(1),
                  base_width = 42/cm(1), dpi = 1200)




PLOT_ALL<-cowplot::plot_grid(plot_genetic_normal_ALL,
                                   plot_genetic_poisson_ALL,
                                   plot_genetic_binomial_ALL,
                                   plot_nongenetic_normal_ALL,
                                   plot_nongenetic_poisson_ALL,
                                   plot_nongenetic_binomial_ALL,
                          #labels=c("A", "B"), 
                          #label_size = 15,
                          ncol =3, nrow = 2,
                     #    hjust = 0, vjust = 1,
                          scale = c(1,  1))
PLOT_ALL



#Save plot
name_plot<-paste0("Simul_powertest_",
      nb_simul,"nbsimul_",nb_per_SA,
      "nbsimulperSA.pdf")
cowplot::save_plot(file = here::here("figures",name_plot ),
                  PLOT_ALL, base_height = 20/cm(1), 
                  base_width = 42/cm(1), dpi = 1200)

```









# REAL DESIGN
#Dataset
```{r } 
#unbalanced dataset
data_PERF <- read.table(file=here::here("data", "DATACOMPLET_PERF.csv"), sep=",", header=TRUE)
data_PERF$Original_environment<-as.factor(data_PERF$Original_environment)
data_PERF <- data_PERF[data_PERF$Original_environment!="WT3",]
data_PERF <- data_PERF[data_PERF$Test_environment!="GF",]
data_PERF <- data_PERF[data_PERF$Test_environment!="Grape",] #mvrnom doesn't work with unbalanced matrix
data_PERF <- droplevels(data_PERF)
tapply(data_PERF$Population, list(data_PERF$Generation, data_PERF$Population), length)
```



# Normal distribution
## Simulation
```{r } 
#Simul data 
nb_simul <- 1000
sim <-  sapply(1:nb_simul, simul_fitnessdata_unbalanced, distrib = "normal", 
               unbalanced_dataset = data_PERF, sdpop = 0.5, 
              sdfruithab = 0.5, sdfruithab_ng = 0.5, rho = -0.05, rho_ng = -0.05, 
              sigma = 0.5)
sim <- as.data.frame(t(sim))
sim <- add_indic_sign(sim)
sim <- add_sim_number_SA(sim)
```




## Plot
```{r } 
####################################
###### Plot genetic
####################################
#Number of simuls for each SA value
tapply(sim$index_SA_Gen, sim$SA_Gen, length)

#Save the same number of simuls for each SA value
nb_per_SA=10
sim_select_genetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_genet = sort(unique(sim_select_genetic$SA_Gen)), 
                 prop_val_sign = tapply(sim_select_genetic$IndicGen, 
                                        sim_select_genetic$SA_Gen, mean), 
                 prop_val_sign_aov = tapply(sim_select_genetic$IndicGen_aov, 
                                        sim_select_genetic$SA_Gen, mean))


#Plot
plot_genetic_normal_unbalanced_real<-ggplot2::ggplot(data = data_prop, 
                                                     aes(x=val_SA_genet)) + 
   geom_point(aes(y=prop_val_sign, color="LMER"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign, color="LMER"), size = 1, linetype = "dotted") + 
   geom_point(aes(y=prop_val_sign_aov, color="Anova"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign_aov, color="Anova"), size = 1, linetype = "dotted") + 
   ylab("Proportion of simulations with\nsignificant genetic local adaption")  +
   xlab("Intensity of genetic local adaptation (SA)")  +
   ggtitle("Normal data (unbalanced experimental design)") +
   theme_LO_sober +
   labs(color = "Methods", linetype = "Design") +
   scale_color_manual(values = colors) +
   scale_linetype_manual(values = lines)
plot_genetic_normal_unbalanced_real




################################# 
### Plot non-genetic
#################################
#Number of simuls for each SA non genetic value
tapply(sim$index_SA_NonGen, sim$SA_NonGen, length)

#Save the same number of simuls for each SA value
nb_per_SA 
sim_select_nongenetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "non-genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_nongenet = sort(unique(sim_select_nongenetic$SA_NonGen)), 
                 prop_val_sign = tapply(sim_select_nongenetic$IndicNonGen, 
                                        sim_select_nongenetic$SA_NonGen, mean), 
                 prop_val_sign_aov = tapply(sim_select_nongenetic$IndicNonGen_aov, 
                                        sim_select_nongenetic$SA_NonGen, mean))


#Plot
plot_nongenetic_normal_unbalanced_real<-ggplot2::ggplot(data = data_prop, 
                                                   aes(x=val_SA_nongenet)) + 
   geom_point(aes(y=prop_val_sign, color="LMER"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign, color="LMER"), size = 1, linetype = "dotted") + 
   geom_point(aes(y=prop_val_sign_aov, color="Anova"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign_aov, color="Anova"), size = 1, linetype = "dotted") + 
   ylab("Proportion of simulations with\nsignificant non-genetic local adaption")  +
   xlab("Intensity of non-genetic local adaptation (SA)")  +
   theme_LO_sober + 
   ggtitle("Normal data (unbalanced experimental design)") +
   labs(color = "Methods") +
   scale_color_manual(values = colors)
plot_nongenetic_normal_unbalanced_real





```




# Poisson distribution
## Simulation
```{r } 
#Simul data 
#nb_simul <- 1000
sim <- sapply(1:nb_simul, simul_fitnessdata_unbalanced, distrib = "poisson", 
              unbalanced_dataset = data_PERF, sdpop = 0.5, 
              sdfruithab = 1, sdfruithab_ng = 1, rho = -0.05, rho_ng = -0.05, sigma = 0.5)
sim <- as.data.frame(t(sim))
sim <- add_indic_sign(sim)
sim <- add_sim_number_SA(sim)
```




## Plot
```{r } 
####################################
###### Plot genetic
####################################
#Number of simuls for each SA value
tapply(sim$index_SA_Gen, sim$SA_Gen, length)

#Save the same number of simuls for each SA value
nb_per_SA=10
sim_select_genetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_genet = sort(unique(sim_select_genetic$SA_Gen)), 
                 prop_val_sign = tapply(sim_select_genetic$IndicGen, 
                                        sim_select_genetic$SA_Gen, mean), 
                 prop_val_sign_aov = tapply(sim_select_genetic$IndicGen_aov, 
                                        sim_select_genetic$SA_Gen, mean))


#Plot
plot_genetic_poisson_unbalanced_real<-ggplot2::ggplot(data = data_prop, 
                                                      aes(x=val_SA_genet)) + 
   geom_point(aes(y=prop_val_sign, color="LMER"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign, color="LMER"), size = 1, linetype = "dotted") + 
   geom_point(aes(y=prop_val_sign_aov, color="Anova"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign_aov, color="Anova"), size = 1, linetype = "dotted") + 
   ylab("Proportion of simulations with\nsignificant genetic local adaption")  +
   xlab("Intensity of genetic local adaptation (SA)")  +
   ggtitle("Poisson data (unbalanced experimental design)") +
   theme_LO_sober  + 
   labs(color = "Methods") +
   scale_color_manual(values = colors)
plot_genetic_poisson_unbalanced_real





################################# 
### Plot non-genetic
#################################
#Number of simuls for each SA non genetic value
tapply(sim$index_SA_NonGen, sim$SA_NonGen, length)

#Save the same number of simuls for each SA value
nb_per_SA 
sim_select_nongenetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "non-genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_nongenet = sort(unique(sim_select_nongenetic$SA_NonGen)), 
                 prop_val_sign = tapply(sim_select_nongenetic$IndicNonGen, 
                                        sim_select_nongenetic$SA_NonGen, mean), 
                 prop_val_sign_aov = tapply(sim_select_nongenetic$IndicNonGen_aov, 
                                        sim_select_nongenetic$SA_NonGen, mean))


colors<-c("LMER" = "#DCA237", "Anova" = "#459B76")
#Plot
plot_nongenetic_poisson_unbalanced_real<-ggplot2::ggplot(data = data_prop, 
                                                   aes(x=val_SA_nongenet)) + 
   geom_point(aes(y=prop_val_sign, color="LMER"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign, color="LMER"), size = 1, linetype = "dotted") + 
   geom_point(aes(y=prop_val_sign_aov, color="Anova"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign_aov, color="Anova"), size = 1, linetype = "dotted") + 
   ylab("Proportion of simulations with\nsignificant non-genetic local adaption")  +
   xlab("Intensity of non-genetic local adaptation (SA)")  +
   theme_LO_sober + 
   ggtitle("Poisson data (unbalanced experimental design)") +
   labs(color = "Methods") +
   scale_color_manual(values = colors)
plot_nongenetic_poisson_unbalanced_real




```






# Binomial distribution
## Simulation
```{r } 
#Simul data 
#nb_simul <- 1000
sim <- sapply(1:nb_simul, simul_fitnessdata_unbalanced, distrib = "binomial", 
              unbalanced_dataset = data_PERF, sdpop = 0.5, 
              sdfruithab = 0.5, sdfruithab_ng = 0.5, 
              rho = -0.05, rho_ng = -0.05, sigma = 0.5)
sim <- as.data.frame(t(sim))
sim <- add_indic_sign(sim)
sim <- add_sim_number_SA(sim)
```




## Plot
```{r } 
####################################
###### Plot genetic
####################################
#Number of simuls for each SA value
tapply(sim$index_SA_Gen, sim$SA_Gen, length)

#Save the same number of simuls for each SA value
nb_per_SA=10
sim_select_genetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_genet = sort(unique(sim_select_genetic$SA_Gen)), 
                 prop_val_sign = tapply(sim_select_genetic$IndicGen, 
                                        sim_select_genetic$SA_Gen, mean), 
                 prop_val_sign_aov = tapply(sim_select_genetic$IndicGen_aov, 
                                        sim_select_genetic$SA_Gen, mean))


#Plot
plot_genetic_Binomial_unbalanced_real<-ggplot2::ggplot(data = data_prop, 
                                                  aes(x=val_SA_genet)) + 
   geom_point(aes(y=prop_val_sign, color="LMER"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign, color="LMER"), size = 1, linetype = "dotted") + 
   geom_point(aes(y=prop_val_sign_aov, color="Anova"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign_aov, color="Anova"), size = 1, linetype = "dotted") + 
   ylab("Proportion of simulations with\nsignificant genetic local adaption")  +
   xlab("Intensity of genetic local adaptation (SA)")  +
   ggtitle("Binomial data (unbalanced experimental design)") +
   theme_LO_sober  + 
   labs(color = "Methods") +
   scale_color_manual(values = colors) 
plot_genetic_Binomial_unbalanced_real



################################# 
### Plot non-genetic
#################################
#Number of simuls for each SA non genetic value
tapply(sim$index_SA_NonGen, sim$SA_NonGen, length)

#Save the same number of simuls for each SA value
nb_per_SA 
sim_select_nongenetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "non-genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_nongenet = sort(unique(sim_select_nongenetic$SA_NonGen)), 
                 prop_val_sign = tapply(sim_select_nongenetic$IndicNonGen, 
                                        sim_select_nongenetic$SA_NonGen, mean), 
                 prop_val_sign_aov = tapply(sim_select_nongenetic$IndicNonGen_aov, 
                                        sim_select_nongenetic$SA_NonGen, mean))


colors<-c("LMER" = "#DCA237", "Anova" = "#459B76")
#Plot
plot_nongenetic_Binomial_unbalanced_real<-ggplot2::ggplot(data = data_prop, 
                                                   aes(x=val_SA_nongenet)) + 
   geom_point(aes(y=prop_val_sign, color="LMER"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign, color="LMER"), size = 1, linetype = "dotted") + 
   geom_point(aes(y=prop_val_sign_aov, color="Anova"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign_aov, color="Anova"), size = 1, linetype = "dotted") + 
   ylab("Proportion of simulations with\nsignificant non-genetic local adaption")  +
   xlab("Intensity of non-genetic local adaptation (SA)")  +
   theme_LO_sober + 
   ggtitle("Binomial data (unbalanced experimental design)") +
   labs(color = "Methods") +
   scale_color_manual(values = colors)
plot_nongenetic_Binomial_unbalanced_real



```



# All plots unbalanced
```{r } 
power_plot_all_unbalanced_real<-cowplot::plot_grid(plot_nongenetic_normal_unbalanced_real,
                                   plot_nongenetic_poisson_unbalanced_real,
                                   plot_nongenetic_Binomial_unbalanced_real,
                                   plot_genetic_normal_unbalanced_real,
                                   plot_genetic_poisson_unbalanced_real,
                                   plot_genetic_Binomial_unbalanced_real,
                          #labels=c("A", "B"), 
                          #label_size = 15,
                          ncol =3, nrow = 2,
                     #    hjust = 0, vjust = 1,
                          scale = c(1,  1))
power_plot_all_unbalanced_real



#Save plot
name_plot<-paste0("Simul_powertest_ALLDATA_UNBALANCED_real",
      nb_simul,"nbsimul_",nb_per_SA,
      "nbsimulperSA.pdf")
# cowplot::save_plot(file =here::here("figures",name_plot ),
#                   power_plot_all_unbalanced_real, base_height = 20/cm(1),
#                   base_width = 42/cm(1), dpi = 1200)
# 

```



