---
title: "Simulations fitness data"
author: "Laure Olazcuaga, Nicolas Rode"
date: "`r format(Sys.Date(), '%d-%B-%Y')`"
output: 
  html_document:
    theme: "journal"
    toc: true
    toc_depth: 3
    number_sections: true
    toc_float:
      collapsed: false
      smooth_scroll: false
editor_options: 
  chunk_output_type: console
---


```{r setup, include =FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
devtools::load_all()
```

# COLORS plot
```{r } 
colors <- c("LMER" = "#DCA237", "Anova" = "#459B76")
lines <- c("Balanced" = "solid", "Unbalanced" = "dotted")
```

# ESTIMATES VARIANCE REAL DATA
```{r } 
#############################
#PERFORMANCE PARAMETERS VALUE
#############################
data_PERF <- read.table(file=here::here("data", "DATACOMPLET_PERF.csv"), sep=",", header=TRUE)
data_PERF$Original_environment<-as.factor(data_PERF$Original_environment)
data_PERF <- data_PERF[data_PERF$Original_environment!="WT3",]
data_PERF <- data_PERF[data_PERF$Test_environment!="GF",]
data_PERF$Test_environment <- as.factor(data_PERF$Test_environment)
data_PERF$Population <- as.factor(data_PERF$Population)
data_PERF <- data_PERF[data_PERF$Test_environment!="Grape",] 
data_PERF <- droplevels(data_PERF)
data_PERF$IndicG0<-as.numeric(ifelse (as.character(data_PERF$Gen) == "G0", 1, 0))

nfruit_data <- nlevels(data_PERF$Original_environment)
nhab_data <- nlevels(data_PERF$Test_environment)
npop_per_fruit_data <- nlevels(data_PERF$Population)/nfruit_data
nrep_data <- mean(tapply(data_PERF$Nb_adults,list(data_PERF$Population,
                                                  data_PERF$Test_environment, 
                                                  data_PERF$Generation),length),na.rm = TRUE)
ntrial_data <- mean(data_PERF$Nb_eggs, na.rm = TRUE)
                              

#POISSON VARIANCE VALUE
mperf_poisson <- lme4::lmer(log(Nb_adults+1) ~ 1+ (1|Population) + 
                               (1|Original_environment:Test_environment) + 
                               (1|Original_environment:Test_environment:IndicG0),
                            data = data_PERF)

sdpop_datapoisson <- sqrt(unlist(lme4::VarCorr(mperf_poisson))[1])                               
sdfruithab_datapoisson <- sqrt(unlist(lme4::VarCorr(mperf_poisson))[3])
sdfruithab_ng_datapoisson <- sqrt(unlist(lme4::VarCorr(mperf_poisson))[2])   
sdfruithab_datapoisson <- sdfruithab_ng_datapoisson
sigma_datapoisson <- sigma(mperf_poisson)


#BINOMIAL VARIANCE VALUE
data_PERF_rate <- data_PERF[data_PERF$Nb_eggs>=data_PERF$Nb_adults,]
mperf_binomial <- lme4::lmer(asin(sqrt(Nb_adults/Nb_eggs)) ~ 1+ (1|Population) + 
                               (1|Original_environment:Test_environment) + 
                               (1|Original_environment:Test_environment:IndicG0),
                            data = data_PERF_rate)

sdpop_databinomial <- sqrt(unlist(lme4::VarCorr(mperf_binomial))[1])                               
sdfruithab_databinomial <- sqrt(unlist(lme4::VarCorr(mperf_binomial))[3])
sdfruithab_ng_databinomial <- sqrt(unlist(lme4::VarCorr(mperf_binomial))[2])   
sdfruithab_databinomial <- sdfruithab_ng_databinomial
sigma_databinomial <- sigma(mperf_binomial)




###########################
#PREFERENCE PARAMETERS VALUE
###########################
data_PREF <- read.table(file=here::here("data", "DATACOMPLET_PREF.csv"), sep=",", header=TRUE)
data_PREF$Original_environment<-as.factor(data_PREF$Original_environment)
data_PREF <- data_PREF[data_PREF$Original_environment!="WT3",]
dim(data_PREF)
data_PREF <- data_PREF[data_PREF$Test_environment=="Cranberry"|
                         data_PREF$Test_environment=="Cherry"|
                          data_PREF$Test_environment=="Strawberry",]
data_PREF$Test_environment <- as.factor(data_PREF$Test_environment)
data_PREF$Population <- as.factor(data_PREF$Population)
data_PREF$BoxID <- as.factor(data_PREF$BoxID)
data_PREF$Nb_eggs <- as.numeric(as.character(data_PREF$Nb_eggs))

data_PREF <- droplevels(data_PREF)
data_PREF$IndicG0<-as.numeric(ifelse (as.character(data_PREF$Gen) == "G0", 1, 0))

nfruit_data_box <- nlevels(data_PREF$Original_environment)
nhab_data_box <- nlevels(data_PREF$Test_environment)
npop_per_fruit_data_box <- nlevels(data_PREF$Population)/nfruit_data
nrep_data_box <- mean(tapply(data_PREF$Nb_eggs,list(data_PREF$Population,
                                                  data_PREF$Test_environment, 
                                                  data_PREF$Generation),length),na.rm = TRUE)


#POISSON BOX VARIANCE VALUE
mperf_poisson_box <- lme4::lmer(log(Nb_eggs+1) ~ 1+ (1|Population) + 
                               (1|Original_environment:Test_environment) + 
                               (1|Original_environment:Test_environment:IndicG0) +
                                  (1|BoxID),
                            data = data_PREF)

sdbox_datapoisson_box <- sqrt(unlist(lme4::VarCorr(mperf_poisson_box))[1])
sdpop_datapoisson_box <- sqrt(unlist(lme4::VarCorr(mperf_poisson_box))[2])                              
sdfruithab_datapoisson_box <- sqrt(unlist(lme4::VarCorr(mperf_poisson_box))[4])
sdfruithab_ng_datapoisson_box <- sqrt(unlist(lme4::VarCorr(mperf_poisson_box))[3])   
sdfruithab_datapoisson_box <- sdfruithab_ng_datapoisson_box
sigma_datapoisson_box <- sigma(mperf_poisson_box)

 

```

#NUMBER OF SIMULS
```{r } 
# Power Analyses
nb_simul <- 100
#Save the same number of simuls for each SA value
nb_per_SA <- 1000
# 
# #Number of simuls for each SA non-genetic value
# tapply(sim$index_SA_NonGen, sim$SA_NonGen, length)

#False positive rate 
nb_simul_fpr <- 10000
```



# BALANCED AND UNBALANCED DESIGN
## Normal distribution
### Balanced
```{r } 
#Perform siluations
sim1 <- sapply(1:nb_simul, simul_fitnessdata, distrib = "normal", design = "balanced",
              rho = -0.05, rho_ng = -0.05, 
              npop_per_fruit = npop_per_fruit_data, 
              nfruit = nfruit_data, nhab = nhab_data, 
              nrep = nrep_data, sdpop = 0.5, sdfruithab = 0.5, sdfruithab_ng = 0.5, sigma = 0.5)
sim1 <- as.data.frame(t(sim1))

sim2 <- sapply(1:nb_simul, simul_fitnessdata, distrib = "normal", design = "balanced",
              rho = -0.5, rho_ng = -0.5, 
              npop_per_fruit = npop_per_fruit_data, nfruit = nfruit_data, 
              nhab = nhab_data, 
              nrep = nrep_data, sdpop = 0.5, sdfruithab = 0.5, sdfruithab_ng = 0.5, 
              sigma = 0.5)
sim2 <- as.data.frame(t(sim2))


sim3 <- sapply(1:nb_simul, simul_fitnessdata, distrib = "normal", design = "balanced",
              rho = 0, rho_ng = 0, 
              npop_per_fruit = npop_per_fruit_data, nfruit = nfruit_data, nhab = nhab_data, 
              nrep = nrep_data, sdpop = 0.5, sdfruithab = 0.5, sdfruithab_ng = 0.5, sigma = 0.5)
sim3 <- as.data.frame(t(sim3))

# Concatenate value
sim <- rbind(sim1,sim2, sim3)

#Add indic SA
sim <- add_indic_sign(sim)

#Add number of simul for each SA value to keep only 100 simuls per SA value
sim <- add_sim_number_SA(sim)



## Local adaptation (genetic)
tapply(sim$IndicGen[sim$index_SA_Gen<101], sim$SA_Gen[sim$index_SA_Gen<101], length)
tapply(sim$IndicGen_aov[sim$index_SA_Gen<101], sim$SA_Gen[sim$index_SA_Gen<101], mean)

## Local adaptation (non-genetic)
tapply(sim$IndicNonGen[sim$index_SA_NonGen<101], sim$SA_NonGen[sim$index_SA_NonGen<101], mean)
tapply(sim$IndicNonGen_aov[sim$index_SA_NonGen<101], sim$SA_NonGen[sim$index_SA_NonGen<101], mean)

tapply(sim$IndicGen, sim$SA_Gen, length)
tapply(sim$IndicNonGen, sim$SA_NonGen, length)


####################################
###### Plot genetic
####################################
#Number of simuls for each SA value
tapply(sim$index_SA_Gen, sim$SA_Gen, length)


sim_select_genetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_genet = sort(unique(sim_select_genetic$SA_Gen)), 
                 prop_val_sign = tapply(sim_select_genetic$IndicGen, 
                                        sim_select_genetic$SA_Gen, mean), 
                 prop_val_sign_aov = tapply(sim_select_genetic$IndicGen_aov, 
                                        sim_select_genetic$SA_Gen, mean))
data_prop$design <- 0
data_prop_gen <- data_prop

#Plot
plot_genetic_normal<-ggplot2::ggplot(data = data_prop, aes(x=val_SA_genet)) + 
   geom_point(aes(y=prop_val_sign, color="LMER"), size = 4) + 
   geom_line(aes(y=prop_val_sign, color="LMER", linetype = "Balanced"), size = 1.5) + 
   geom_point(aes(y=prop_val_sign_aov, color="Anova"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign_aov, color="Anova", linetype = "Balanced"), size = 0.75) + 
   ylab("Proportion of simulations with\nsignificant genetic local adaption")  +
   xlab("Intensity of genetic local adaptation (SA)")  +
   ggtitle("Normal data") +
   theme_LO_sober  + 
   ggtitle("Normal data") +
   labs(color = "Methods", linetype = "Design") +
   scale_color_manual(values = colors) +
   scale_linetype_manual(values = lines)
plot_genetic_normal



################################# 
### Plot non-genetic
#################################
#Save the same number of simuls for each SA value
sim_select_nongenetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "non-genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_nongenet = sort(unique(sim_select_nongenetic$SA_NonGen)), 
                 prop_val_sign = tapply(sim_select_nongenetic$IndicNonGen, 
                                        sim_select_nongenetic$SA_NonGen, mean), 
                 prop_val_sign_aov = tapply(sim_select_nongenetic$IndicNonGen_aov, 
                                        sim_select_nongenetic$SA_NonGen, mean))
data_prop$design <- 0
data_prop_nongen <- data_prop

#Plot
plot_nongenetic_normal<-ggplot2::ggplot(data = data_prop, aes(x=val_SA_nongenet)) + 
   geom_point(aes(y=prop_val_sign, color="LMER"), size = 4) + 
   geom_line(aes(y=prop_val_sign, color="LMER", linetype = "Balanced"), size = 1.5) + 
   geom_point(aes(y=prop_val_sign_aov, color="Anova"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign_aov, color="Anova", linetype = "Balanced"), size = 0.75) + 
   ylab("Proportion of simulations with\nsignificant non-genetic local adaption")  +
   xlab("Intensity of non-genetic local adaptation (SA)")  +
   theme_LO_sober + 
   ggtitle("Normal data") +
   labs(color = "Methods", linetype = "Design") +
   scale_color_manual(values = colors) +
   scale_linetype_manual(values = lines)
plot_nongenetic_normal


```



### Unbalanced (low)
```{r } 
#Perform siluations
sim1 <- sapply(1:nb_simul, simul_fitnessdata, distrib = "normal", 
              design = "unbalanced", disp_design = 1,
              rho = -0.5, rho_ng = -0.5, 
              npop_per_fruit = npop_per_fruit_data, nfruit = nfruit_data, nhab = nhab_data, 
              nrep = nrep_data, sdpop = 0.5, sdfruithab = 0.5, sdfruithab_ng = 0.5, sigma = 0.5)
sim1 <- as.data.frame(t(sim1))
#Perform siluations
sim2 <- sapply(1:nb_simul, simul_fitnessdata, distrib = "normal", 
              design = "unbalanced", disp_design = 1,
              rho = 0, rho_ng = 0, 
              npop_per_fruit = npop_per_fruit_data, nfruit = nfruit_data, nhab = nhab_data, 
              nrep = nrep_data, sdpop = 0.5, sdfruithab = 0.5, sdfruithab_ng = 0.5, sigma = 0.5)
sim2 <- as.data.frame(t(sim2))
#Perform siluations
sim3 <- sapply(1:nb_simul, simul_fitnessdata, distrib = "normal", 
              design = "unbalanced", disp_design = 1,
              rho = -0.05, rho_ng = -0.05, 
              npop_per_fruit = npop_per_fruit_data, nfruit = nfruit_data, nhab = nhab_data, 
              nrep = nrep_data, sdpop = 0.5, sdfruithab = 0.5, sdfruithab_ng = 0.5, sigma = 0.5)
sim3 <- as.data.frame(t(sim3))

# Concatenate value
sim <- rbind(sim1,sim2, sim3)
sim <- add_indic_sign(sim)
sim <- add_sim_number_SA(sim)




####################################
###### Plot genetic
####################################
#Number of simuls for each SA value
# tapply(sim$index_SA_Gen, sim$SA_Gen, length)
# nb_per_SA

sim_select_genetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_genet = sort(unique(sim_select_genetic$SA_Gen)), 
                 prop_val_sign = tapply(sim_select_genetic$IndicGen, 
                                        sim_select_genetic$SA_Gen, mean), 
                 prop_val_sign_aov = tapply(sim_select_genetic$IndicGen_aov, 
                                        sim_select_genetic$SA_Gen, mean))
data_prop$design <- 1
data_prop_gen <- rbind(data_prop_gen,data_prop)

#Plot
plot_genetic_normal<-ggplot2::ggplot(data = data_prop, aes(x=val_SA_genet)) + 
   geom_point(aes(y=prop_val_sign, color="LMER"), size = 4) + 
   geom_line(aes(y=prop_val_sign, color="LMER", linetype = "Unbalanced"), size = 1.5) + 
   geom_point(aes(y=prop_val_sign_aov, color="Anova"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign_aov, color="Anova", linetype = "Unbalanced"), size = 0.75) + 
   ylab("Proportion of simulations with\nsignificant genetic local adaption")  +
   xlab("Intensity of genetic local adaptation (SA)")  +
   ggtitle("Normal data") +
   theme_LO_sober  + 
   ggtitle("Normal data") +
   labs(color = "Methods", linetype = "Design") +
   scale_color_manual(values = colors) +
   scale_linetype_manual(values = lines)
plot_genetic_normal



################################# 
### Plot non-genetic
#################################
#Save the same number of simuls for each SA value
sim_select_nongenetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "non-genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_nongenet = sort(unique(sim_select_nongenetic$SA_NonGen)), 
                 prop_val_sign = tapply(sim_select_nongenetic$IndicNonGen, 
                                        sim_select_nongenetic$SA_NonGen, mean), 
                 prop_val_sign_aov = tapply(sim_select_nongenetic$IndicNonGen_aov, 
                                        sim_select_nongenetic$SA_NonGen, mean))
data_prop$design <- 1
data_prop_nongen <- rbind(data_prop_nongen,data_prop)

#Plot
plot_nongenetic_normal<-ggplot2::ggplot(data = data_prop, aes(x=val_SA_nongenet)) + 
   geom_point(aes(y=prop_val_sign, color="LMER"), size = 4) + 
   geom_line(aes(y=prop_val_sign, color="LMER", linetype = "Unbalanced"), size = 1.5) + 
   geom_point(aes(y=prop_val_sign_aov, color="Anova"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign_aov, color="Anova", linetype = "Unbalanced"), size = 0.75) + 
   ylab("Proportion of simulations with\nsignificant non-genetic local adaption")  +
   xlab("Intensity of non-genetic local adaptation (SA)")  +
   theme_LO_sober + 
   ggtitle("Normal data") +
   labs(color = "Methods", linetype = "Design") +
   scale_color_manual(values = colors) +
   scale_linetype_manual(values = lines)
plot_nongenetic_normal


```



### Unbalanced (high)
```{r } 
#Perform siluations
sim1 <- sapply(1:nb_simul, simul_fitnessdata, distrib = "normal", 
              design = "unbalanced", disp_design = 4,
              rho = -0.5, rho_ng = -0.5, 
              npop_per_fruit = npop_per_fruit_data, nfruit = nfruit_data, nhab = nhab_data, 
              nrep = nrep_data, sdpop = 0.5, sdfruithab = 0.5, sdfruithab_ng = 0.5, sigma = 0.5)
sim1 <- as.data.frame(t(sim1))
#Perform siluations
sim2 <- sapply(1:nb_simul, simul_fitnessdata, distrib = "normal", 
              design = "unbalanced", disp_design = 4,
              rho = 0, rho_ng = 0, 
              npop_per_fruit = npop_per_fruit_data, nfruit = nfruit_data, nhab = nhab_data, 
              nrep = nrep_data, sdpop = 0.5, sdfruithab = 0.5, sdfruithab_ng = 0.5, sigma = 0.5)
sim2 <- as.data.frame(t(sim2))
#Perform siluations
sim3 <- sapply(1:nb_simul, simul_fitnessdata, distrib = "normal", 
              design = "unbalanced", disp_design = 4,
              rho = -0.05, rho_ng = -0.05, 
              npop_per_fruit = npop_per_fruit_data, nfruit = nfruit_data, nhab = nhab_data, 
              nrep = nrep_data, sdpop = 0.5, sdfruithab = 0.5, sdfruithab_ng = 0.5, sigma = 0.5)
sim3 <- as.data.frame(t(sim3))
# Concatenate value
sim <- rbind(sim1,sim2, sim3)
sim <- add_indic_sign(sim)
sim <- add_sim_number_SA(sim)




####################################
###### Plot genetic
####################################
#Number of simuls for each SA value
# tapply(sim$index_SA_Gen, sim$SA_Gen, length)
# nb_per_SA

sim_select_genetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_genet = sort(unique(sim_select_genetic$SA_Gen)), 
                 prop_val_sign = tapply(sim_select_genetic$IndicGen, 
                                        sim_select_genetic$SA_Gen, mean), 
                 prop_val_sign_aov = tapply(sim_select_genetic$IndicGen_aov, 
                                        sim_select_genetic$SA_Gen, mean))
data_prop$design <- 4
data_prop_gen <- rbind(data_prop_gen,data_prop)

#Plot
plot_genetic_normal<-ggplot2::ggplot(data = data_prop, aes(x=val_SA_genet)) + 
   geom_point(aes(y=prop_val_sign, color="LMER"), size = 4) + 
   geom_line(aes(y=prop_val_sign, color="LMER", linetype = "Unbalanced"), size = 1.5) + 
   geom_point(aes(y=prop_val_sign_aov, color="Anova"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign_aov, color="Anova", linetype = "Unbalanced"), size = 0.75) + 
   ylab("Proportion of simulations with\nsignificant genetic local adaption")  +
   xlab("Intensity of genetic local adaptation (SA)")  +
   ggtitle("Normal data") +
   theme_LO_sober  + 
   ggtitle("Normal data") +
   labs(color = "Methods", linetype = "Design") +
   scale_color_manual(values = colors) +
   scale_linetype_manual(values = lines)
plot_genetic_normal



################################# 
### Plot non-genetic
#################################
#Save the same number of simuls for each SA value
sim_select_nongenetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "non-genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_nongenet = sort(unique(sim_select_nongenetic$SA_NonGen)), 
                 prop_val_sign = tapply(sim_select_nongenetic$IndicNonGen, 
                                        sim_select_nongenetic$SA_NonGen, mean), 
                 prop_val_sign_aov = tapply(sim_select_nongenetic$IndicNonGen_aov, 
                                        sim_select_nongenetic$SA_NonGen, mean))
data_prop$design <- 4
data_prop_nongen <- rbind(data_prop_nongen,data_prop)

#Plot
plot_nongenetic_normal<-ggplot2::ggplot(data = data_prop, aes(x=val_SA_nongenet)) + 
   geom_point(aes(y=prop_val_sign, color="LMER"), size = 4) + 
   geom_line(aes(y=prop_val_sign, color="LMER", linetype = "Unbalanced"), size = 1.5) + 
   geom_point(aes(y=prop_val_sign_aov, color="Anova"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign_aov, color="Anova", linetype = "Unbalanced"), size = 0.75) + 
   ylab("Proportion of simulations with\nsignificant non-genetic local adaption")  +
   xlab("Intensity of non-genetic local adaptation (SA)")  +
   theme_LO_sober + 
   ggtitle("Normal data") +
   labs(color = "Methods", linetype = "Design") +
   scale_color_manual(values = colors) +
   scale_linetype_manual(values = lines)
plot_nongenetic_normal


```


### Plot
```{r }

data_proportion_gen<-tidyr::gather(data_prop_gen, "method", "proportion", 2:3)
data_proportion_gen$method <- plyr::revalue(data_proportion_gen$method, 
                                      c("prop_val_sign"="LMER", "prop_val_sign_aov"="Anova"))
data_proportion_gen$design <- as.factor(data_proportion_gen$design)


#Plot genetic
plot_genetic_normal_balancedvsunbalanced<-ggplot2::ggplot(data = data_proportion_gen, 
   aes(x = val_SA_genet, y = proportion, color = method, linetype = design)) + 
   geom_point(size = 2) + 
   geom_line(size = 1) + 
   ylab("Proportion of simulations with\nsignificant genetic local adaption")  +
   xlab("Intensity of genetic local adaptation (SA)")  +
   ggtitle("Normal data") +
   ylim(0,1) +
   theme_LO_sober  + 
   ggtitle("Normal data") + 
   labs(color = "Methods", linetype = "Unbalanced\ndesign") +
   scale_color_manual(values = c("#459B76","#DCA237")) +
   scale_linetype_manual(values = c("solid","dashed","dotted"))
plot_genetic_normal_balancedvsunbalanced


#Data non-genetic 
data_proportion_nongen<-tidyr::gather(data_prop_nongen, "method", "proportion", 2:3)
data_proportion_nongen$method <- plyr::revalue(data_proportion_nongen$method, 
                                      c("prop_val_sign"="LMER", "prop_val_sign_aov"="Anova"))
data_proportion_nongen$design <- as.factor(data_proportion_nongen$design)

#Plot non-genetic
plot_nongenetic_normal_balancedvsunbalanced<-ggplot2::ggplot(data = data_proportion_nongen, 
   aes(x = val_SA_nongenet, y = proportion, color = method, linetype = design)) + 
   geom_point(size = 2) + 
   geom_line(size = 1) + 
   ylab("Proportion of simulations with\nsignificant non-genetic local adaption")  +
   xlab("Intensity of non-genetic local adaptation (SA)")  +
   ggtitle("Normal data") +
   ylim(0,1) +
   theme_LO_sober  + 
   ggtitle("Normal data") + 
   labs(color = "Methods", linetype = "Unbalanced\ndesign") +
   scale_color_manual(values = c("#459B76","#DCA237")) +
   scale_linetype_manual(values = c("solid","dashed","dotted"))
plot_nongenetic_normal_balancedvsunbalanced


```




### False positive rate analyses
#### No genetic and no non-genetic effects
```{r } 
sim <- sapply(1:nb_simul_fpr, simul_fitnessdata, distrib = "normal", design = "balanced",
              rho=0, rho_ng=0, 
              npop_per_fruit = npop_per_fruit_data, nfruit = nfruit_data, nhab = nhab_data, 
              nrep = nrep_data, sdpop = 0.5, sdfruithab = 0.5, sdfruithab_ng = 0.5, sigma = 0.5)

sim <- as.data.frame(t(sim))
sim <- add_indic_sign(sim)
  
## Local adaptation (genetic)
mean(sim$IndicGen)
mean(sim$IndicGen_aov)

## Local adaptation (non-genetic)
mean(sim$IndicNonGen)
mean(sim$IndicNonGen_aov)


```



#### Genetic effects and no non-genetic effects
```{r } 
sim <- sapply(1:nb_simul_fpr, simul_fitnessdata, distrib = "normal", design = "balanced",
              rho=-0.1, rho_ng=0,  
              npop_per_fruit = npop_per_fruit_data, nfruit = nfruit_data, nhab = nhab_data, 
              nrep = nrep_data, sdpop = 0.5, sdfruithab = 0.5, sdfruithab_ng = 0.5, sigma = 0.5)

sim <- as.data.frame(t(sim))
sim <- add_indic_sign(sim)

## Local adaptation (genetic)
tapply(sim$IndicGen, sim$SA_Gen, length)
tapply(sim$IndicGen_aov, sim$SA_Gen, mean)

## Local adaptation (non-genetic)
mean(sim$IndicNonGen)
mean(sim$IndicNonGen_aov)

tapply(sim$IndicNonGen, sim$SA_Gen, mean)
tapply(sim$IndicNonGen_aov, sim$SA_Gen, mean)

tapply(sim$IndicNonGen, sim$SA_NonGen, mean)
tapply(sim$IndicNonGen_aov, sim$SA_NonGen, mean)

```



#### Non-genetic effects and no genetic effects
```{r } 
sim <- sapply(1:nb_simul_fpr, simul_fitnessdata, distrib = "normal",
              design = "balanced",
              rho=0, rho_ng=-0.1,  
              npop_per_fruit = npop_per_fruit_data, nfruit = nfruit_data, 
              nhab = nhab_data, 
              nrep = nrep_data, sdpop = 0.5, sdfruithab = 0.5, sdfruithab_ng = 0.5, 
              sigma = 0.5)
sim <- as.data.frame(t(sim))
sim <- add_indic_sign(sim)

## Local adaptation (genetic)
mean(sim$IndicGen)
mean(sim$IndicGen_aov)

tapply(sim$IndicGen, sim$SA_Gen, mean)
tapply(sim$IndicGen_aov, sim$SA_Gen, mean)

tapply(sim$IndicGen, sim$SA_NonGen, mean)
tapply(sim$IndicGen_aov, sim$SA_NonGen, mean)

## Local adaptation (non-genetic)
tapply(sim$IndicNonGen, sim$SA_NonGen, mean)
tapply(sim$IndicNonGen_aov, sim$SA_NonGen, mean)

```





## Poisson distribution
### Balanced
```{r } 
rm(sim)
rm(data_proportion_gen, data_proportion_nongen, 
   sim_select_genetic, sim_select_nongenetic,
   data_prop, data_prop_gen, data_prop_nongen)

#Perform siluations
sim1 <- sapply(1:nb_simul, simul_fitnessdata, distrib = "poisson", design = "balanced",
              rho = 0, rho_ng = 0, 
              npop_per_fruit = npop_per_fruit_data, nfruit = nfruit_data, nhab = nhab_data, 
              nrep = nrep_data, sdpop = sdpop_datapoisson, 
              sdfruithab = sdfruithab_datapoisson, 
              sdfruithab_ng = sdfruithab_ng_datapoisson, 
              sigma = sigma_datapoisson)
sim1 <- as.data.frame(t(sim1))

#Perform siluations
sim2 <- sapply(1:nb_simul, simul_fitnessdata, distrib = "poisson", design = "balanced",
              rho = -0.05, rho_ng = -0.05, 
              npop_per_fruit = npop_per_fruit_data, nfruit = nfruit_data, 
              nhab = nhab_data, 
              nrep = nrep_data, sdpop = sdpop_datapoisson, 
              sdfruithab = sdfruithab_datapoisson, 
              sdfruithab_ng = sdfruithab_ng_datapoisson, 
              sigma = sigma_datapoisson)
sim2 <- as.data.frame(t(sim2))

#Perform siluations
sim3 <- sapply(1:nb_simul, simul_fitnessdata, distrib = "poisson", design = "balanced",
              rho = -0.5, rho_ng = -0.5, 
              npop_per_fruit = npop_per_fruit_data, nfruit = nfruit_data, nhab = nhab_data, 
              nrep = nrep_data, sdpop = sdpop_datapoisson, 
              sdfruithab = sdfruithab_datapoisson, sdfruithab_ng = sdfruithab_ng_datapoisson, 
              sigma = sigma_datapoisson)
sim3 <- as.data.frame(t(sim3))

# Concatenate value
sim <- rbind(sim1,sim2, sim3)

#Add indic SA
sim <- add_indic_sign(sim)

#Add number of simul for each SA value to keep only 100 simuls per SA value
sim <- add_sim_number_SA(sim)


## Local adaptation (genetic)
tapply(sim$IndicGen[sim$index_SA_Gen<101], sim$SA_Gen[sim$index_SA_Gen<101], length)
tapply(sim$IndicGen_aov[sim$index_SA_Gen<101], sim$SA_Gen[sim$index_SA_Gen<101], mean)

## Local adaptation (non-genetic)
tapply(sim$IndicNonGen[sim$index_SA_NonGen<101], sim$SA_NonGen[sim$index_SA_NonGen<101], mean)
tapply(sim$IndicNonGen_aov[sim$index_SA_NonGen<101], sim$SA_NonGen[sim$index_SA_NonGen<101], mean)

tapply(sim$IndicGen, sim$SA_Gen, length)
tapply(sim$IndicNonGen, sim$SA_NonGen, length)


####################################
###### Plot genetic
####################################
#Number of simuls for each SA value
tapply(sim$index_SA_Gen, sim$SA_Gen, length)


sim_select_genetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_genet = sort(unique(sim_select_genetic$SA_Gen)), 
                 prop_val_sign = tapply(sim_select_genetic$IndicGen, 
                                        sim_select_genetic$SA_Gen, mean), 
                 prop_val_sign_aov = tapply(sim_select_genetic$IndicGen_aov, 
                                        sim_select_genetic$SA_Gen, mean))
data_prop$design <- 0
data_prop_gen <- data_prop

#Plot
plot_genetic_poisson<-ggplot2::ggplot(data = data_prop, aes(x=val_SA_genet)) + 
   geom_point(aes(y=prop_val_sign, color="LMER"), size = 4) + 
   geom_line(aes(y=prop_val_sign, color="LMER", linetype = "Balanced"), size = 1.5) + 
   geom_point(aes(y=prop_val_sign_aov, color="Anova"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign_aov, color="Anova", linetype = "Balanced"), size = 0.75) + 
   ylab("Proportion of simulations with\nsignificant genetic local adaption")  +
   xlab("Intensity of genetic local adaptation (SA)")  +
   ggtitle("Poisson data") +
   theme_LO_sober  + 
   ggtitle("Poisson data") +
   labs(color = "Methods", linetype = "Design") +
   scale_color_manual(values = colors) +
   scale_linetype_manual(values = lines)
plot_genetic_poisson




################################# 
### Plot non-genetic
#################################
#Save the same number of simuls for each SA value
sim_select_nongenetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "non-genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_nongenet = sort(unique(sim_select_nongenetic$SA_NonGen)), 
                 prop_val_sign = tapply(sim_select_nongenetic$IndicNonGen, 
                                        sim_select_nongenetic$SA_NonGen, mean), 
                 prop_val_sign_aov = tapply(sim_select_nongenetic$IndicNonGen_aov, 
                                        sim_select_nongenetic$SA_NonGen, mean))
data_prop$design <- 0
data_prop_nongen <- data_prop

#Plot
plot_nongenetic_poisson<-ggplot2::ggplot(data = data_prop, aes(x=val_SA_nongenet)) + 
   geom_point(aes(y=prop_val_sign, color="LMER"), size = 4) + 
   geom_line(aes(y=prop_val_sign, color="LMER", linetype = "Balanced"), size = 1.5) + 
   geom_point(aes(y=prop_val_sign_aov, color="Anova"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign_aov, color="Anova", linetype = "Balanced"), size = 0.75) + 
   ylab("Proportion of simulations with\nsignificant non-genetic local adaption")  +
   xlab("Intensity of non-genetic local adaptation (SA)")  +
   theme_LO_sober + 
   ggtitle("Poisson data") +
   labs(color = "Methods", linetype = "Design") +
   scale_color_manual(values = colors) +
   scale_linetype_manual(values = lines)
plot_nongenetic_poisson


```



### Unbalanced (low)
```{r } 
#Perform siluations
sim1 <- sapply(1:nb_simul, simul_fitnessdata, distrib = "poisson",
              design = "unbalanced", disp_design = 1,
              rho = 0, rho_ng = 0, 
              npop_per_fruit = npop_per_fruit_data, nfruit = nfruit_data, nhab = nhab_data, 
              nrep = nrep_data, sdpop = sdpop_datapoisson, 
              sdfruithab = sdfruithab_datapoisson, sdfruithab_ng = sdfruithab_ng_datapoisson, 
              sigma = sigma_datapoisson)


sim1 <- as.data.frame(t(sim1))

#Perform siluations
sim2 <- sapply(1:nb_simul, simul_fitnessdata, distrib = "poisson",
              design = "unbalanced", disp_design = 1,
              rho = -0.5, rho_ng = -0.5, 
              npop_per_fruit = npop_per_fruit_data, nfruit = nfruit_data, nhab = nhab_data, 
              nrep = nrep_data, sdpop = sdpop_datapoisson, 
              sdfruithab = sdfruithab_datapoisson, sdfruithab_ng = sdfruithab_ng_datapoisson, 
              sigma = sigma_datapoisson)


sim2 <- as.data.frame(t(sim2))
#Perform siluations
sim3 <- sapply(1:nb_simul, simul_fitnessdata, distrib = "poisson",
              design = "unbalanced", disp_design = 1,
              rho = -0.05, rho_ng = -0.05, 
              npop_per_fruit = npop_per_fruit_data, nfruit = nfruit_data, nhab = nhab_data, 
              nrep = nrep_data, sdpop = sdpop_datapoisson, 
              sdfruithab = sdfruithab_datapoisson, sdfruithab_ng = sdfruithab_ng_datapoisson, 
              sigma = sigma_datapoisson)


sim3 <- as.data.frame(t(sim3))
# Concatenate value
sim <- rbind(sim1,sim2, sim3)
sim <- add_indic_sign(sim)
sim <- add_sim_number_SA(sim)




####################################
###### Plot genetic
####################################
#Number of simuls for each SA value
# tapply(sim$index_SA_Gen, sim$SA_Gen, length)
# nb_per_SA

sim_select_genetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_genet = sort(unique(sim_select_genetic$SA_Gen)), 
                 prop_val_sign = tapply(sim_select_genetic$IndicGen, 
                                        sim_select_genetic$SA_Gen, mean), 
                 prop_val_sign_aov = tapply(sim_select_genetic$IndicGen_aov, 
                                        sim_select_genetic$SA_Gen, mean))
data_prop$design <- 1
data_prop_gen <- rbind(data_prop_gen,data_prop)

#Plot
plot_genetic_poisson_unbalanced<-ggplot2::ggplot(data = data_prop, aes(x=val_SA_genet)) + 
   geom_point(aes(y=prop_val_sign, color="LMER"), size = 4) + 
   geom_line(aes(y=prop_val_sign, color="LMER", linetype = "Unbalanced"), size = 1.5) + 
   geom_point(aes(y=prop_val_sign_aov, color="Anova"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign_aov, color="Anova", linetype = "Unbalanced"), size = 0.75) + 
   ylab("Proportion of simulations with\nsignificant genetic local adaption")  +
   xlab("Intensity of genetic local adaptation (SA)")  +
   ggtitle("Poisson data") +
   theme_LO_sober  + 
   labs(color = "Methods", linetype = "Design") +
   scale_color_manual(values = colors) +
   scale_linetype_manual(values = lines)
plot_genetic_poisson_unbalanced



################################# 
### Plot non-genetic
#################################
#Save the same number of simuls for each SA value
sim_select_nongenetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "non-genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_nongenet = sort(unique(sim_select_nongenetic$SA_NonGen)), 
                 prop_val_sign = tapply(sim_select_nongenetic$IndicNonGen, 
                                        sim_select_nongenetic$SA_NonGen, mean), 
                 prop_val_sign_aov = tapply(sim_select_nongenetic$IndicNonGen_aov, 
                                        sim_select_nongenetic$SA_NonGen, mean))
data_prop$design <- 1
data_prop_nongen <- rbind(data_prop_nongen,data_prop)

#Plot
plot_nongenetic_poisson_unbalanced<-ggplot2::ggplot(data = data_prop, aes(x=val_SA_nongenet)) + 
   geom_point(aes(y=prop_val_sign, color="LMER"), size = 4) + 
   geom_line(aes(y=prop_val_sign, color="LMER", linetype = "Unbalanced"), size = 1.5) + 
   geom_point(aes(y=prop_val_sign_aov, color="Anova"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign_aov, color="Anova", linetype = "Unbalanced"), size = 0.75) + 
   ylab("Proportion of simulations with\nsignificant non-genetic local adaption")  +
   xlab("Intensity of non-genetic local adaptation (SA)")  +
   theme_LO_sober + 
   ggtitle("Poisson data") +
   labs(color = "Methods", linetype = "Design") +
   scale_color_manual(values = colors) +
   scale_linetype_manual(values = lines)
plot_nongenetic_poisson_unbalanced


```



### Unbalanced (high)
```{r } 
#Perform siluations
sim1 <- sapply(1:nb_simul, simul_fitnessdata, distrib = "poisson",
              design = "unbalanced", disp_design = 4,
              rho = 0, rho_ng = 0, 
              npop_per_fruit = npop_per_fruit_data, nfruit = nfruit_data, nhab = nhab_data, 
              nrep = nrep_data, sdpop = sdpop_datapoisson, 
              sdfruithab = sdfruithab_datapoisson, sdfruithab_ng = sdfruithab_ng_datapoisson, 
              sigma = sigma_datapoisson)
sim1 <- as.data.frame(t(sim1))
#Perform siluations
sim2 <- sapply(1:nb_simul, simul_fitnessdata, distrib = "poisson",
              design = "unbalanced", disp_design = 4,
              rho = -0.5, rho_ng = -0.5, 
              npop_per_fruit = npop_per_fruit_data, nfruit = nfruit_data, nhab = nhab_data, 
              nrep = nrep_data, sdpop = sdpop_datapoisson, 
              sdfruithab = sdfruithab_datapoisson, sdfruithab_ng = sdfruithab_ng_datapoisson, 
              sigma = sigma_datapoisson)
sim2 <- as.data.frame(t(sim2))
#Perform siluations
sim3 <- sapply(1:nb_simul, simul_fitnessdata, distrib = "poisson",
              design = "unbalanced", disp_design = 4,
              rho = -0.05, rho_ng = -0.05, 
              npop_per_fruit = npop_per_fruit_data, nfruit = nfruit_data, nhab = nhab_data, 
              nrep = nrep_data, sdpop = sdpop_datapoisson, 
              sdfruithab = sdfruithab_datapoisson, sdfruithab_ng = sdfruithab_ng_datapoisson, 
              sigma = sigma_datapoisson)
sim3 <- as.data.frame(t(sim3))
# Concatenate value
sim <- rbind(sim1,sim2, sim3)
sim <- add_indic_sign(sim)
sim <- add_sim_number_SA(sim)




####################################
###### Plot genetic
####################################
#Number of simuls for each SA value
# tapply(sim$index_SA_Gen, sim$SA_Gen, length)
# nb_per_SA

sim_select_genetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_genet = sort(unique(sim_select_genetic$SA_Gen)), 
                 prop_val_sign = tapply(sim_select_genetic$IndicGen, 
                                        sim_select_genetic$SA_Gen, mean), 
                 prop_val_sign_aov = tapply(sim_select_genetic$IndicGen_aov, 
                                        sim_select_genetic$SA_Gen, mean))
data_prop$design <- 4
data_prop_gen <- rbind(data_prop_gen,data_prop)

#Plot
plot_genetic_poisson_unbalanced_high<-ggplot2::ggplot(data = data_prop, aes(x=val_SA_genet)) + 
   geom_point(aes(y=prop_val_sign, color="LMER"), size = 4) + 
   geom_line(aes(y=prop_val_sign, color="LMER", linetype = "Unbalanced"), size = 1.5) + 
   geom_point(aes(y=prop_val_sign_aov, color="Anova"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign_aov, color="Anova", linetype = "Unbalanced"), size = 0.75) + 
   ylab("Proportion of simulations with\nsignificant genetic local adaption")  +
   xlab("Intensity of genetic local adaptation (SA)")  +
   ggtitle("Poisson data") +
   theme_LO_sober  + 
   labs(color = "Methods", linetype = "Design") +
   scale_color_manual(values = colors) +
   scale_linetype_manual(values = lines)
plot_genetic_poisson_unbalanced_high



################################# 
### Plot non-genetic
#################################
#Save the same number of simuls for each SA value
sim_select_nongenetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "non-genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_nongenet = sort(unique(sim_select_nongenetic$SA_NonGen)), 
                 prop_val_sign = tapply(sim_select_nongenetic$IndicNonGen, 
                                        sim_select_nongenetic$SA_NonGen, mean), 
                 prop_val_sign_aov = tapply(sim_select_nongenetic$IndicNonGen_aov, 
                                        sim_select_nongenetic$SA_NonGen, mean))
data_prop$design <- 4
data_prop_nongen <- rbind(data_prop_nongen,data_prop)

#Plot
plot_nongenetic_poisson_unbalanced_high<-ggplot2::ggplot(data = data_prop, aes(x=val_SA_nongenet)) + 
   geom_point(aes(y=prop_val_sign, color="LMER"), size = 4) + 
   geom_line(aes(y=prop_val_sign, color="LMER", linetype = "Unbalanced"), size = 1.5) + 
   geom_point(aes(y=prop_val_sign_aov, color="Anova"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign_aov, color="Anova", linetype = "Unbalanced"), size = 0.75) + 
   ylab("Proportion of simulations with\nsignificant non-genetic local adaption")  +
   xlab("Intensity of non-genetic local adaptation (SA)")  +
   theme_LO_sober + 
   ggtitle("Poisson data") +
   labs(color = "Methods", linetype = "Design") +
   scale_color_manual(values = colors) +
   scale_linetype_manual(values = lines)
plot_nongenetic_poisson_unbalanced_high

```


### Plot
```{r }

data_proportion_gen<-tidyr::gather(data_prop_gen, "method", "proportion", 2:3)
data_proportion_gen$method <- plyr::revalue(data_proportion_gen$method, 
                                      c("prop_val_sign"="LMER", "prop_val_sign_aov"="Anova"))
data_proportion_gen$design <- as.factor(data_proportion_gen$design)


#Plot genetic
plot_genetic_poisson_balancedvsunbalanced<-ggplot2::ggplot(data = data_proportion_gen, 
   aes(x = val_SA_genet, y = proportion, color = method, linetype = design)) + 
   geom_point(size = 2) + 
   geom_line(size = 1) + 
   ylab("Proportion of simulations with\nsignificant genetic local adaption")  +
   xlab("Intensity of genetic local adaptation (SA)")  +
   ggtitle("Poisson data") +
   ylim(0,1) +
   theme_LO_sober  + 
   labs(color = "Methods", linetype = "Unbalanced\ndesign") +
   scale_color_manual(values = c("#459B76","#DCA237")) +
   scale_linetype_manual(values = c("solid","dashed","dotted"))
plot_genetic_poisson_balancedvsunbalanced


#Data non-genetic 
data_proportion_nongen<-tidyr::gather(data_prop_nongen, "method", "proportion", 2:3)
data_proportion_nongen$method <- plyr::revalue(data_proportion_nongen$method, 
                                      c("prop_val_sign"="LMER", "prop_val_sign_aov"="Anova"))
data_proportion_nongen$design <- as.factor(data_proportion_nongen$design)

#Plot non-genetic
plot_nongenetic_poisson_balancedvsunbalanced<-ggplot2::ggplot(data = data_proportion_nongen, 
   aes(x = val_SA_nongenet, y = proportion, color = method, linetype = design)) + 
   geom_point(size = 2) + 
   geom_line(size = 1) + 
   ylim(0,1) +
   ylab("Proportion of simulations with\nsignificant non-genetic local adaption")  +
   xlab("Intensity of non-genetic local adaptation (SA)")  +
   ggtitle("Poisson data") +
   theme_LO_sober  + 
   ggtitle("Poisson data") + 
   labs(color = "Methods", linetype = "Unbalanced\ndesign") +
   scale_color_manual(values = c("#459B76","#DCA237")) +
   scale_linetype_manual(values = c("solid","dashed","dotted"))
plot_nongenetic_poisson_balancedvsunbalanced


```









### False positive rate analyses
#### No genetic and no non-genetic effects
```{r } 
sim <- sapply(1:nb_simul_fpr, simul_fitnessdata, distrib = "poisson", design = "balanced",
              rho=0, rho_ng=0,   
              npop_per_fruit = npop_per_fruit_data, nfruit = nfruit_data, nhab = nhab_data, 
              nrep = nrep_data, sdpop = sdpop_datapoisson, 
              sdfruithab = sdfruithab_datapoisson, sdfruithab_ng = sdfruithab_ng_datapoisson, 
              sigma = sigma_datapoisson)

sim <- as.data.frame(t(sim))
sim <- add_indic_sign(sim)
  
## Local adaptation (genetic)
mean(sim$IndicGen)
mean(sim$IndicGen_aov)

## Local adaptation (non-genetic)
mean(sim$IndicNonGen)
mean(sim$IndicNonGen_aov)

```



#### Genetic effects and no non-genetic effects
```{r } 
sim <- sapply(1:nb_simul_fpr, simul_fitnessdata, distrib = "poisson", design = "balanced",
              rho=-0.1, rho_ng=0,   
              npop_per_fruit = npop_per_fruit_data, nfruit = nfruit_data, nhab = nhab_data, 
              nrep = nrep_data, sdpop = sdpop_datapoisson, 
              sdfruithab = sdfruithab_datapoisson, sdfruithab_ng = sdfruithab_ng_datapoisson, 
              sigma = sigma_datapoisson)

sim <- as.data.frame(t(sim))
sim <- add_indic_sign(sim)

## Local adaptation (genetic)
tapply(sim$IndicGen, sim$SA_Gen, mean)
tapply(sim$IndicGen_aov, sim$SA_Gen, mean)

## Local adaptation (non-genetic)
mean(sim$IndicNonGen)
mean(sim$IndicNonGen_aov)


```



#### Non-genetic effects and no genetic effects
```{r } 
sim <- sapply(1:nb_simul_fpr, simul_fitnessdata, distrib = "poisson",design = "balanced",
              rho=0, rho_ng=-0.1,  
              npop_per_fruit = npop_per_fruit_data, nfruit = nfruit_data, nhab = nhab_data, 
              nrep = nrep_data, sdpop = sdpop_datapoisson, 
              sdfruithab = sdfruithab_datapoisson, sdfruithab_ng = sdfruithab_ng_datapoisson, 
              sigma = sigma_datapoisson)

sim <- as.data.frame(t(sim))
sim <- add_indic_sign(sim)

## Local adaptation (genetic)
mean(sim$IndicGen)
mean(sim$IndicGen_aov)

## Local adaptation (non-genetic)
tapply(sim$IndicNonGen, sim$SA_NonGen, mean)
tapply(sim$IndicNonGen_aov, sim$SA_NonGen, mean)

```










## Binomial distribution 
### Balanced
```{r } 
rm(sim)
rm(data_proportion_gen, data_proportion_nongen, 
   sim_select_genetic, sim_select_nongenetic,
   data_prop, data_prop_gen, data_prop_nongen)

#Perform siluations
sim1 <- sapply(1:nb_simul, simul_fitnessdata, distrib = "binomial", design = "balanced",
              rho = -0.05, rho_ng = -0.05, 
              npop_per_fruit = npop_per_fruit_data, 
              nfruit = nfruit_data, nhab = nhab_data, 
              nrep = nrep_data, sdpop = sdpop_databinomial,
              sdfruithab = sdfruithab_databinomial, 
              sdfruithab_ng = sdfruithab_ng_databinomial, 
              sigma = sigma_databinomial)
sim1 <- as.data.frame(t(sim1))
#Perform siluations
sim2 <- sapply(1:nb_simul, simul_fitnessdata, distrib = "binomial", design = "balanced",
              rho = 0, rho_ng = 0, 
              npop_per_fruit = npop_per_fruit_data, nfruit = nfruit_data, nhab = nhab_data, 
              nrep = nrep_data, sdpop = sdpop_databinomial,
              sdfruithab = sdfruithab_databinomial, sdfruithab_ng = sdfruithab_ng_databinomial, 
              sigma = sigma_databinomial)
sim2 <- as.data.frame(t(sim2))
#Perform siluations
sim3 <- sapply(1:nb_simul, simul_fitnessdata, distrib = "binomial", design = "balanced",
              rho = -0.5, rho_ng = -0.5, 
              npop_per_fruit = npop_per_fruit_data, nfruit = nfruit_data, nhab = nhab_data, 
              nrep = nrep_data, sdpop = sdpop_databinomial,
              sdfruithab = sdfruithab_databinomial, 
              sdfruithab_ng = sdfruithab_ng_databinomial, 
              sigma = sigma_databinomial)
sim3 <- as.data.frame(t(sim3))


# Concatenate value
sim <- rbind(sim1,sim2, sim3)


#Add indic SA
sim <- add_indic_sign(sim)

#Add number of simul for each SA value to keep only 100 simuls per SA value
sim <- add_sim_number_SA(sim)


## Local adaptation (genetic)
tapply(sim$IndicGen[sim$index_SA_Gen<101], sim$SA_Gen[sim$index_SA_Gen<101], length)
tapply(sim$IndicGen_aov[sim$index_SA_Gen<101], sim$SA_Gen[sim$index_SA_Gen<101], mean)

## Local adaptation (non-genetic)
tapply(sim$IndicNonGen[sim$index_SA_NonGen<101], sim$SA_NonGen[sim$index_SA_NonGen<101], mean)
tapply(sim$IndicNonGen_aov[sim$index_SA_NonGen<101], sim$SA_NonGen[sim$index_SA_NonGen<101], mean)

tapply(sim$IndicGen, sim$SA_Gen, length)
tapply(sim$IndicNonGen, sim$SA_NonGen, length)


####################################
###### Plot genetic
####################################
#Number of simuls for each SA value
tapply(sim$index_SA_Gen, sim$SA_Gen, length)


sim_select_genetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_genet = sort(unique(sim_select_genetic$SA_Gen)), 
                 prop_val_sign = tapply(sim_select_genetic$IndicGen, 
                                        sim_select_genetic$SA_Gen, mean), 
                 prop_val_sign_aov = tapply(sim_select_genetic$IndicGen_aov, 
                                        sim_select_genetic$SA_Gen, mean))
data_prop$design <- 0
data_prop_gen <- data_prop

#Plot
plot_genetic_binomial<-ggplot2::ggplot(data = data_prop, aes(x=val_SA_genet)) + 
   geom_point(aes(y=prop_val_sign, color="LMER"), size = 4) + 
   geom_line(aes(y=prop_val_sign, color="LMER", linetype = "Balanced"), size = 1.5) + 
   geom_point(aes(y=prop_val_sign_aov, color="Anova"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign_aov, color="Anova", linetype = "Balanced"), size = 0.75) + 
   ylab("Proportion of simulations with\nsignificant genetic local adaption")  +
   xlab("Intensity of genetic local adaptation (SA)")  +
   ggtitle("Binomial data") +
   theme_LO_sober  + 
   labs(color = "Methods", linetype = "Design") +
   scale_color_manual(values = colors) +
   scale_linetype_manual(values = lines)
plot_genetic_binomial



################################# 
### Plot non-genetic
#################################
#Save the same number of simuls for each SA value
sim_select_nongenetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "non-genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_nongenet = sort(unique(sim_select_nongenetic$SA_NonGen)), 
                 prop_val_sign = tapply(sim_select_nongenetic$IndicNonGen, 
                                        sim_select_nongenetic$SA_NonGen, mean), 
                 prop_val_sign_aov = tapply(sim_select_nongenetic$IndicNonGen_aov, 
                                        sim_select_nongenetic$SA_NonGen, mean))
data_prop$design <- 0
data_prop_nongen <- data_prop

#Plot
plot_nongenetic_binomial<-ggplot2::ggplot(data = data_prop, aes(x=val_SA_nongenet)) + 
   geom_point(aes(y=prop_val_sign, color="LMER"), size = 4) + 
   geom_line(aes(y=prop_val_sign, color="LMER", linetype = "Balanced"), size = 1.5) + 
   geom_point(aes(y=prop_val_sign_aov, color="Anova"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign_aov, color="Anova", linetype = "Balanced"), size = 0.75) + 
   ylab("Proportion of simulations with\nsignificant non-genetic local adaption")  +
   xlab("Intensity of non-genetic local adaptation (SA)")  +
   theme_LO_sober + 
   ggtitle("Binomial data") +
   labs(color = "Methods", linetype = "Design") +
   scale_color_manual(values = colors) +
   scale_linetype_manual(values = lines)
plot_nongenetic_binomial


```



### Unbalanced (low)
```{r } 
#Perform siluations
sim1 <- sapply(1:nb_simul, simul_fitnessdata, distrib = "binomial",
              design = "unbalanced", disp_design = 1,
              rho = -0.5, rho_ng = -0.5, 
              npop_per_fruit = npop_per_fruit_data, nfruit = nfruit_data, nhab = nhab_data, 
              nrep = nrep_data, sdpop = sdpop_databinomial,
              sdfruithab = sdfruithab_databinomial, sdfruithab_ng = sdfruithab_ng_databinomial, 
              sigma = sigma_databinomial)
sim1 <- as.data.frame(t(sim1))
#Perform siluations
sim2 <- sapply(1:nb_simul, simul_fitnessdata, distrib = "binomial",
              design = "unbalanced", disp_design = 1,
              rho = 0, rho_ng = 0, 
              npop_per_fruit = npop_per_fruit_data, nfruit = nfruit_data, nhab = nhab_data, 
              nrep = nrep_data, sdpop = sdpop_databinomial,
              sdfruithab = sdfruithab_databinomial, sdfruithab_ng = sdfruithab_ng_databinomial, 
              sigma = sigma_databinomial)
sim2 <- as.data.frame(t(sim2))

#Perform siluations
sim3 <- sapply(1:nb_simul, simul_fitnessdata, distrib = "binomial",
              design = "unbalanced", disp_design = 1,
              rho = -0.05, rho_ng = -0.05, 
              npop_per_fruit = npop_per_fruit_data, nfruit = nfruit_data, nhab = nhab_data, 
              nrep = nrep_data, sdpop = sdpop_databinomial,
              sdfruithab = sdfruithab_databinomial, sdfruithab_ng = sdfruithab_ng_databinomial, 
              sigma = sigma_databinomial)
sim3 <- as.data.frame(t(sim3))

# Concatenate value
sim <- rbind(sim1,sim2, sim3)
sim <- add_indic_sign(sim)
sim <- add_sim_number_SA(sim)




####################################
###### Plot genetic
####################################
#Number of simuls for each SA value
# tapply(sim$index_SA_Gen, sim$SA_Gen, length)
# nb_per_SA

sim_select_genetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_genet = sort(unique(sim_select_genetic$SA_Gen)), 
                 prop_val_sign = tapply(sim_select_genetic$IndicGen, 
                                        sim_select_genetic$SA_Gen, mean), 
                 prop_val_sign_aov = tapply(sim_select_genetic$IndicGen_aov, 
                                        sim_select_genetic$SA_Gen, mean))
data_prop$design <- 1
data_prop_gen <- rbind(data_prop_gen,data_prop)

#Plot
plot_genetic_binomial_unbalanced<-ggplot2::ggplot(data = data_prop, aes(x=val_SA_genet)) + 
   geom_point(aes(y=prop_val_sign, color="LMER"), size = 4) + 
   geom_line(aes(y=prop_val_sign, color="LMER", linetype = "Unbalanced"), size = 1.5) + 
   geom_point(aes(y=prop_val_sign_aov, color="Anova"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign_aov, color="Anova", linetype = "Unbalanced"), size = 0.75) + 
   ylab("Proportion of simulations with\nsignificant genetic local adaption")  +
   xlab("Intensity of genetic local adaptation (SA)")  +
   ggtitle("Binomial data") +
   theme_LO_sober  + 
   labs(color = "Methods", linetype = "Design") +
   scale_color_manual(values = colors) +
   scale_linetype_manual(values = lines)
plot_genetic_binomial_unbalanced



################################# 
### Plot non-genetic
#################################
#Save the same number of simuls for each SA value
sim_select_nongenetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "non-genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_nongenet = sort(unique(sim_select_nongenetic$SA_NonGen)), 
                 prop_val_sign = tapply(sim_select_nongenetic$IndicNonGen, 
                                        sim_select_nongenetic$SA_NonGen, mean), 
                 prop_val_sign_aov = tapply(sim_select_nongenetic$IndicNonGen_aov, 
                                        sim_select_nongenetic$SA_NonGen, mean))
data_prop$design <- 1
data_prop_nongen <- rbind(data_prop_nongen,data_prop)

#Plot
plot_nongenetic_binomial_unbalanced<-ggplot2::ggplot(data = data_prop, aes(x=val_SA_nongenet)) + 
   geom_point(aes(y=prop_val_sign, color="LMER"), size = 4) + 
   geom_line(aes(y=prop_val_sign, color="LMER", linetype = "Unbalanced"), size = 1.5) + 
   geom_point(aes(y=prop_val_sign_aov, color="Anova"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign_aov, color="Anova", linetype = "Unbalanced"), size = 0.75) + 
   ylab("Proportion of simulations with\nsignificant non-genetic local adaption")  +
   xlab("Intensity of non-genetic local adaptation (SA)")  +
   theme_LO_sober + 
   ggtitle("Binomial data") +
   labs(color = "Methods", linetype = "Design") +
   scale_color_manual(values = colors) +
   scale_linetype_manual(values = lines)
plot_nongenetic_binomial_unbalanced


```



### Unbalanced (high)
```{r } 
#Perform siluations
sim1 <- sapply(1:nb_simul, simul_fitnessdata, distrib = "binomial",
              design = "unbalanced", disp_design = 4,
              rho = 0, rho_ng = 0, 
              npop_per_fruit = npop_per_fruit_data, nfruit = nfruit_data, nhab = nhab_data, 
              nrep = nrep_data, sdpop = sdpop_databinomial,
              sdfruithab = sdfruithab_databinomial, sdfruithab_ng = sdfruithab_ng_databinomial, 
              sigma = sigma_databinomial)
sim1 <- as.data.frame(t(sim1))
#Perform siluations
sim2 <- sapply(1:nb_simul, simul_fitnessdata, distrib = "binomial",
              design = "unbalanced", disp_design = 4,
              rho = -0.05, rho_ng = -0.05, 
              npop_per_fruit = npop_per_fruit_data, nfruit = nfruit_data, nhab = nhab_data, 
              nrep = nrep_data, sdpop = sdpop_databinomial,
              sdfruithab = sdfruithab_databinomial, sdfruithab_ng = sdfruithab_ng_databinomial, 
              sigma = sigma_databinomial)
sim2 <- as.data.frame(t(sim2))
#Perform siluations
sim3 <- sapply(1:nb_simul, simul_fitnessdata, distrib = "binomial",
              design = "unbalanced", disp_design = 4,
              rho = -0.5, rho_ng = -0.5, 
              npop_per_fruit = npop_per_fruit_data, nfruit = nfruit_data, nhab = nhab_data, 
              nrep = nrep_data, sdpop = sdpop_databinomial,
              sdfruithab = sdfruithab_databinomial, sdfruithab_ng = sdfruithab_ng_databinomial, 
              sigma = sigma_databinomial)
sim3 <- as.data.frame(t(sim3))

# Concatenate value
sim <- rbind(sim1,sim2, sim3)
sim <- add_indic_sign(sim)
sim <- add_sim_number_SA(sim)




####################################
###### Plot genetic
####################################
#Number of simuls for each SA value
# tapply(sim$index_SA_Gen, sim$SA_Gen, length)
# nb_per_SA

sim_select_genetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_genet = sort(unique(sim_select_genetic$SA_Gen)), 
                 prop_val_sign = tapply(sim_select_genetic$IndicGen, 
                                        sim_select_genetic$SA_Gen, mean), 
                 prop_val_sign_aov = tapply(sim_select_genetic$IndicGen_aov, 
                                        sim_select_genetic$SA_Gen, mean))
data_prop$design <- 4
data_prop_gen <- rbind(data_prop_gen,data_prop)

#Plot
plot_genetic_binomial_unbalanced_high<-ggplot2::ggplot(data = data_prop, aes(x=val_SA_genet)) + 
   geom_point(aes(y=prop_val_sign, color="LMER"), size = 4) + 
   geom_line(aes(y=prop_val_sign, color="LMER", linetype = "Unbalanced"), size = 1.5) + 
   geom_point(aes(y=prop_val_sign_aov, color="Anova"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign_aov, color="Anova", linetype = "Unbalanced"), size = 0.75) + 
   ylab("Proportion of simulations with\nsignificant genetic local adaption")  +
   xlab("Intensity of genetic local adaptation (SA)")  +
   ggtitle("Binomial data") +
   theme_LO_sober  + 
   labs(color = "Methods", linetype = "Design") +
   scale_color_manual(values = colors) +
   scale_linetype_manual(values = lines)
plot_genetic_binomial_unbalanced_high



################################# 
### Plot non-genetic
#################################
#Save the same number of simuls for each SA value
sim_select_nongenetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "non-genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_nongenet = sort(unique(sim_select_nongenetic$SA_NonGen)), 
                 prop_val_sign = tapply(sim_select_nongenetic$IndicNonGen, 
                                        sim_select_nongenetic$SA_NonGen, mean), 
                 prop_val_sign_aov = tapply(sim_select_nongenetic$IndicNonGen_aov, 
                                        sim_select_nongenetic$SA_NonGen, mean))
data_prop$design <- 4
data_prop_nongen <- rbind(data_prop_nongen,data_prop)

#Plot
plot_nongenetic_binomial_unbalanced_high<-ggplot2::ggplot(data = data_prop, aes(x=val_SA_nongenet)) + 
   geom_point(aes(y=prop_val_sign, color="LMER"), size = 4) + 
   geom_line(aes(y=prop_val_sign, color="LMER", linetype = "Unbalanced"), size = 1.5) + 
   geom_point(aes(y=prop_val_sign_aov, color="Anova"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign_aov, color="Anova", linetype = "Unbalanced"), size = 0.75) + 
   ylab("Proportion of simulations with\nsignificant non-genetic local adaption")  +
   xlab("Intensity of non-genetic local adaptation (SA)")  +
   theme_LO_sober + 
   ggtitle("Binomial data") +
   labs(color = "Methods", linetype = "Design") +
   scale_color_manual(values = colors) +
   scale_linetype_manual(values = lines)
plot_nongenetic_binomial_unbalanced_high

```


### Plot
```{r }

data_proportion_gen<-tidyr::gather(data_prop_gen, "method", "proportion", 2:3)
data_proportion_gen$method <- plyr::revalue(data_proportion_gen$method, 
                                      c("prop_val_sign"="LMER", "prop_val_sign_aov"="Anova"))
data_proportion_gen$design <- as.factor(data_proportion_gen$design)


#Plot genetic
plot_genetic_binomial_balancedvsunbalanced<-ggplot2::ggplot(data = data_proportion_gen, 
   aes(x = val_SA_genet, y = proportion, color = method, linetype = design)) + 
   geom_point(size = 2) + 
   geom_line(size = 1) + 
   ylab("Proportion of simulations with\nsignificant genetic local adaption")  +
   xlab("Intensity of genetic local adaptation (SA)")  +
   ggtitle("Binomial data") +
   ylim(0,1) +
   theme_LO_sober  + 
   labs(color = "Methods", linetype = "Unbalanced\ndesign") +
   scale_color_manual(values = c("#459B76","#DCA237")) +
   scale_linetype_manual(values = c("solid","dashed","dotted"))
plot_genetic_binomial_balancedvsunbalanced


#Data non-genetic 
data_proportion_nongen<-tidyr::gather(data_prop_nongen, "method", "proportion", 2:3)
data_proportion_nongen$method <- plyr::revalue(data_proportion_nongen$method, 
                                      c("prop_val_sign"="LMER", "prop_val_sign_aov"="Anova"))
data_proportion_nongen$design <- as.factor(data_proportion_nongen$design)

#Plot non-genetic
plot_nongenetic_binomial_balancedvsunbalanced<-ggplot2::ggplot(data = data_proportion_nongen, 
   aes(x = val_SA_nongenet, y = proportion, color = method, linetype = design)) + 
   geom_point(size = 2) + 
   ylim(0,1) +
   geom_line(size = 1) + 
   ylab("Proportion of simulations with\nsignificant non-genetic local adaption")  +
   xlab("Intensity of non-genetic local adaptation (SA)")  +
   ggtitle("Binomial data") +
   theme_LO_sober  + 
   labs(color = "Methods", linetype = "Unbalanced\ndesign") +
   scale_color_manual(values = c("#459B76","#DCA237")) +
   scale_linetype_manual(values = c("solid","dashed","dotted"))
plot_nongenetic_binomial_balancedvsunbalanced


```





### False positive rate analyses
#### No genetic and no non-genetic effects
```{r } 
sim <- sapply(1:nb_simul_fpr, simul_fitnessdata, distrib = "binomial", design = "balanced",
              rho=0, rho_ng=0, 
              npop_per_fruit = npop_per_fruit_data, nfruit = nfruit_data, nhab = nhab_data, 
              nrep = nrep_data, sdpop = sdpop_databinomial,
              sdfruithab = sdfruithab_databinomial, sdfruithab_ng = sdfruithab_ng_databinomial, 
              sigma = sigma_databinomial)
sim <- as.data.frame(t(sim))
sim <- add_indic_sign(sim)
  
## Local adaptation (genetic)
mean(sim$IndicGen)

mean(sim$IndicGen_aov)

## Local adaptation (non-genetic)
mean(sim$IndicNonGen)
mean(sim$IndicNonGen_aov)


```



#### Genetic effects and no non-genetic effects
```{r } 
sim <- sapply(1:nb_simul_fpr, simul_fitnessdata, distrib = "binomial", design = "balanced",
              rho=-0.1, rho_ng=0,
              npop_per_fruit = npop_per_fruit_data, nfruit = nfruit_data, nhab = nhab_data, 
              nrep = nrep_data, sdpop = sdpop_databinomial,
              sdfruithab = sdfruithab_databinomial, sdfruithab_ng = sdfruithab_ng_databinomial, 
              sigma = sigma_databinomial)
sim <- as.data.frame(t(sim))
sim <- add_indic_sign(sim)

## Local adaptation (genetic)
tapply(sim$IndicGen, sim$SA_Gen, mean)
tapply(sim$IndicGen_aov, sim$SA_Gen, mean)

## Local adaptation (non-genetic)
mean(sim$IndicNonGen)
mean(sim$IndicNonGen_aov)

```



#### non-genetic effects and no genetic effects
```{r } 
### 
sim <- sapply(1:nb_simul_fpr, simul_fitnessdata, distrib = "binomial", design = "balanced",
              rho=0, rho_ng=-0.1,
              npop_per_fruit = npop_per_fruit_data, nfruit = nfruit_data, nhab = nhab_data, 
              nrep = nrep_data, sdpop = sdpop_databinomial,
              sdfruithab = sdfruithab_databinomial, sdfruithab_ng = sdfruithab_ng_databinomial, 
              sigma = sigma_databinomial)
sim <- as.data.frame(t(sim))
sim <- add_indic_sign(sim)

## Local adaptation (genetic)
mean(sim$IndicGen)
mean(sim$IndicGen_aov)

## Local adaptation (non-genetic)
tapply(sim$IndicNonGen, sim$SA_NonGen, mean)
tapply(sim$IndicNonGen_aov, sim$SA_NonGen, mean)

```






# PLOT Balanced vs Unbalanced
```{r } 
POWER_ALL<-cowplot::plot_grid(plot_genetic_normal_balancedvsunbalanced,
                              plot_genetic_poisson_balancedvsunbalanced,
                              plot_genetic_binomial_balancedvsunbalanced,
                              plot_nongenetic_normal_balancedvsunbalanced,
                              plot_nongenetic_poisson_balancedvsunbalanced,
                              plot_nongenetic_binomial_balancedvsunbalanced,
                              ncol = 3, nrow = 2,
                              scale = c(1,  1))
POWER_ALL



#Save plot
name_plot<-paste0("Simul_powertest_ALLDATA_BALANCED_and_UNBALANCED",
      nb_simul,"nbsimul_",nb_per_SA,
      "nbsimulperSA.pdf")
# cowplot::save_plot(file =here::here("figures",name_plot ),
#                   POWER_ALL, base_height = 20/cm(1),
#                   base_width = 40/cm(1), dpi = 1200)




```



# BOX EFFECT Absent vs Present
## Non box
```{r } 
rm(sim)
rm(data_proportion_gen, data_proportion_nongen, 
   sim_select_genetic, sim_select_nongenetic,
   data_prop, data_prop_gen, data_prop_nongen)

#Perform siluations
sim1 <- sapply(1:nb_simul, simul_fitnessdata, distrib = "poisson", design = "balanced",
              rho = -0.5, rho_ng = -0.5, 
              npop_per_fruit = npop_per_fruit_data, nfruit = nfruit_data, nhab = nhab_data, 
              nrep = nrep_data, sdpop = sdpop_datapoisson, 
              sdfruithab = sdfruithab_datapoisson, sdfruithab_ng = sdfruithab_ng_datapoisson, 
              sigma = sigma_datapoisson)
sim1 <- as.data.frame(t(sim1))
sim2 <- sapply(1:nb_simul, simul_fitnessdata, distrib = "poisson", design = "balanced",
              rho = -0.05, rho_ng = -0.05, 
              npop_per_fruit = npop_per_fruit_data, nfruit = nfruit_data, nhab = nhab_data, 
              nrep = nrep_data, sdpop = sdpop_datapoisson, 
              sdfruithab = sdfruithab_datapoisson, sdfruithab_ng = sdfruithab_ng_datapoisson, 
              sigma = sigma_datapoisson)
sim2 <- as.data.frame(t(sim2))
sim3 <- sapply(1:nb_simul, simul_fitnessdata, distrib = "poisson", design = "balanced",
              rho = 0, rho_ng = 0, 
              npop_per_fruit = npop_per_fruit_data, nfruit = nfruit_data, nhab = nhab_data, 
              nrep = nrep_data, sdpop = sdpop_datapoisson, 
              sdfruithab = sdfruithab_datapoisson, sdfruithab_ng = sdfruithab_ng_datapoisson, 
              sigma = sigma_datapoisson)
sim3 <- as.data.frame(t(sim3))


# Concatenate value
sim <- rbind(sim1,sim2, sim3)

sim <- add_indic_sign(sim)
sim <- add_sim_number_SA(sim)

colors <- c("LMER" = "#DCA237", "Anova" = "#459B76")
lines_box <- c("Present" = "dotted", "Absent" = "solid")
####################################
###### Plot genetic
####################################
sim_select_genetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_genet = sort(unique(sim_select_genetic$SA_Gen)), 
                 prop_val_sign = tapply(sim_select_genetic$IndicGen, 
                                        sim_select_genetic$SA_Gen, mean), 
                 prop_val_sign_aov = tapply(sim_select_genetic$IndicGen_aov, 
                                        sim_select_genetic$SA_Gen, mean))
data_prop$sd_box <- 0
data_prop_gen <- data_prop



################################# 
### Plot non-genetic
#################################
#Save the same number of simuls for each SA value
sim_select_nongenetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "non-genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_nongenet = sort(unique(sim_select_nongenetic$SA_NonGen)), 
                 prop_val_sign = tapply(sim_select_nongenetic$IndicNonGen, 
                                        sim_select_nongenetic$SA_NonGen, mean), 
                 prop_val_sign_aov = tapply(sim_select_nongenetic$IndicNonGen_aov, 
                                        sim_select_nongenetic$SA_NonGen, mean))
data_prop$sd_box <- 0
data_prop_nongen <- data_prop





```

## Box (low)
```{r } 
#With lower value of sdbox (close to sdpop): 
sdbox_datapoisson_box
sigma_datapoisson
sdpop_datapoisson
sdfruithab_datapoisson


#Perform siluations
sim1 <- sapply(1:nb_simul, simul_fitnessdata, distrib = "poisson", design = "balanced",
              rho = -0.5, rho_ng = -0.5, 
              npop_per_fruit = npop_per_fruit_data, nfruit = nfruit_data, nhab = nhab_data, 
              nrep = nrep_data, sdpop = sdpop_datapoisson, sdbox = 0.5,
              sdfruithab = sdfruithab_datapoisson, sdfruithab_ng = sdfruithab_ng_datapoisson, 
              sigma = sigma_datapoisson)
sim1 <- as.data.frame(t(sim1))
sim2 <- sapply(1:nb_simul, simul_fitnessdata, distrib = "poisson", design = "balanced",
              rho = 0, rho_ng = 0, 
              npop_per_fruit = npop_per_fruit_data, nfruit = nfruit_data, nhab = nhab_data, 
              nrep = nrep_data, sdpop = sdpop_datapoisson, sdbox = 0.5,
              sdfruithab = sdfruithab_datapoisson, sdfruithab_ng = sdfruithab_ng_datapoisson, 
              sigma = sigma_datapoisson)
sim2 <- as.data.frame(t(sim2))
sim3 <- sapply(1:nb_simul, simul_fitnessdata, distrib = "poisson", design = "balanced",
              rho = -0.05, rho_ng = -0.05, 
              npop_per_fruit = npop_per_fruit_data, nfruit = nfruit_data, nhab = nhab_data, 
              nrep = nrep_data, sdpop = sdpop_datapoisson, sdbox = sdbox_datapoisson_box,
              sdfruithab = sdfruithab_datapoisson, sdfruithab_ng = sdfruithab_ng_datapoisson, 
              sigma = sigma_datapoisson)
sim3 <- as.data.frame(t(sim3))
# Concatenate value
sim <- rbind(sim1,sim2, sim3)

sim <- add_indic_sign(sim)
sim <- add_sim_number_SA(sim)


####################################
###### Plot genetic
####################################
sim_select_genetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_genet = sort(unique(sim_select_genetic$SA_Gen)), 
                 prop_val_sign = tapply(sim_select_genetic$IndicGen, 
                                        sim_select_genetic$SA_Gen, mean), 
                 prop_val_sign_aov = tapply(sim_select_genetic$IndicGen_aov, 
                                        sim_select_genetic$SA_Gen, mean))
data_prop$sd_box <- 0.5
data_prop_gen <- rbind(data_prop_gen,data_prop)


################################# 
### Plot non-genetic
#################################
#Save the same number of simuls for each SA value
sim_select_nongenetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "non-genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_nongenet = sort(unique(sim_select_nongenetic$SA_NonGen)), 
                 prop_val_sign = tapply(sim_select_nongenetic$IndicNonGen, 
                                        sim_select_nongenetic$SA_NonGen, mean), 
                 prop_val_sign_aov = tapply(sim_select_nongenetic$IndicNonGen_aov, 
                                        sim_select_nongenetic$SA_NonGen, mean))
data_prop$sd_box <- 0.5
data_prop_nongen <- rbind(data_prop_nongen,data_prop)

```



## Box (high)
```{r } 
#With lower value of sdbox (close to sdpop): 
sdbox_datapoisson_box
sigma_datapoisson
sdpop_datapoisson
sdfruithab_datapoisson


#Perform siluations
sim1 <- sapply(1:nb_simul, simul_fitnessdata, distrib = "poisson", design = "balanced",
              rho = -0.5, rho_ng = -0.5, 
              npop_per_fruit = npop_per_fruit_data, nfruit = nfruit_data, nhab = nhab_data, 
              nrep = nrep_data, sdpop = sdpop_datapoisson, sdbox = 1.5,
              sdfruithab = sdfruithab_datapoisson, sdfruithab_ng = sdfruithab_ng_datapoisson, 
              sigma = sigma_datapoisson)
sim1 <- as.data.frame(t(sim1))
sim2 <- sapply(1:nb_simul, simul_fitnessdata, distrib = "poisson", design = "balanced",
              rho = 0, rho_ng = 0, 
              npop_per_fruit = npop_per_fruit_data, nfruit = nfruit_data, nhab = nhab_data, 
              nrep = nrep_data, sdpop = sdpop_datapoisson, sdbox = 1.5,
              sdfruithab = sdfruithab_datapoisson, sdfruithab_ng = sdfruithab_ng_datapoisson, 
              sigma = sigma_datapoisson)
sim2 <- as.data.frame(t(sim2))
sim3 <- sapply(1:nb_simul, simul_fitnessdata, distrib = "poisson", design = "balanced",
              rho = -0.05, rho_ng = -0.05, 
              npop_per_fruit = npop_per_fruit_data, nfruit = nfruit_data, nhab = nhab_data, 
              nrep = nrep_data, sdpop = sdpop_datapoisson, sdbox = 1.5,
              sdfruithab = sdfruithab_datapoisson, sdfruithab_ng = sdfruithab_ng_datapoisson, 
              sigma = sigma_datapoisson)
sim3 <- as.data.frame(t(sim3))
# Concatenate value
sim <- rbind(sim1,sim2, sim3)

sim <- add_indic_sign(sim)
sim <- add_sim_number_SA(sim)


####################################
###### Plot genetic
####################################
sim_select_genetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_genet = sort(unique(sim_select_genetic$SA_Gen)), 
                 prop_val_sign = tapply(sim_select_genetic$IndicGen, 
                                        sim_select_genetic$SA_Gen, mean), 
                 prop_val_sign_aov = tapply(sim_select_genetic$IndicGen_aov, 
                                        sim_select_genetic$SA_Gen, mean))

data_prop$sd_box <- 1.5
data_prop_gen <- rbind(data_prop_gen,data_prop)



################################# 
### Plot non-genetic
#################################
#Save the same number of simuls for each SA value
sim_select_nongenetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "non-genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_nongenet = sort(unique(sim_select_nongenetic$SA_NonGen)), 
                 prop_val_sign = tapply(sim_select_nongenetic$IndicNonGen, 
                                        sim_select_nongenetic$SA_NonGen, mean), 
                 prop_val_sign_aov = tapply(sim_select_nongenetic$IndicNonGen_aov, 
                                        sim_select_nongenetic$SA_NonGen, mean))
data_prop$sd_box <- 1.5
data_prop_nongen <- rbind(data_prop_nongen,data_prop)







```



## Plot
```{r } 
#################################
### Common plot
#################################
data_proportion_gen<-tidyr::gather(data_prop_gen, "method", "proportion", 2:3)
data_proportion_gen$method <- plyr::revalue(data_proportion_gen$method, 
                                      c("prop_val_sign"="LMER", "prop_val_sign_aov"="Anova"))
data_proportion_gen$sd_box <- as.factor(data_proportion_gen$sd_box)


#Plot genetic
plot_genetic_poisson_ALL_box<-ggplot2::ggplot(data = data_proportion_gen, 
   aes(x = val_SA_genet, y = proportion, color = method, linetype = sd_box)) + 
   geom_point(size = 2) + 
   ylim(0,1) +
   geom_line(size = 1, alpha = 0.7) + 
   ylab("Proportion of simulations with\nsignificant genetic local adaption")  +
   xlab("Intensity of genetic local adaptation (SA)")  +
   ggtitle("Poisson data") +
   theme_LO_sober  + 
   labs(color = "Methods", linetype = "Box effect\n(sd box)") +
   scale_color_manual(values = c("#459B76","#DCA237")) +
   scale_linetype_manual(values = c("solid","dashed","dotted"))
plot_genetic_poisson_ALL_box




#Data non-genetic 
data_proportion_nongen<-tidyr::gather(data_prop_nongen, "method", "proportion", 2:3)
data_proportion_nongen$method <- plyr::revalue(data_proportion_nongen$method, 
                                      c("prop_val_sign"="LMER", "prop_val_sign_aov"="Anova"))
data_proportion_nongen$sd_box <- as.factor(data_proportion_nongen$sd_box)



#Plot non-genetic
plot_nongenetic_poisson_ALL_box<-ggplot2::ggplot(data = data_proportion_nongen, 
   aes(x = val_SA_nongenet, y = proportion, color = method, linetype = sd_box)) + 
   geom_point(size = 2) + 
   ylim(0,1) +
   geom_line(size = 1) + 
   ylab("Proportion of simulations with\nsignificant non-genetic local adaption")  +
   xlab("Intensity of non-genetic local adaptation (SA)")  +
   ggtitle("Poisson data") +
   theme_LO_sober  + 
   labs(color = "Methods", linetype = "Box effect\n(sd box)") +
   scale_color_manual(values = c("#459B76","#DCA237")) +
   scale_linetype_manual(values = c("solid","dashed","dotted"))
plot_nongenetic_poisson_ALL_box



power_poisson_box<-cowplot::plot_grid(plot_genetic_poisson_ALL_box,
                                      plot_nongenetic_poisson_ALL_box,
                          labels=c("A", "B"), 
                          label_size = 15,
                          ncol =1, nrow = 2,
                     #    hjust = 0, vjust = 1,
                          scale = c(1,  1))
power_poisson_box

#Save plot
name_plot<-paste0("Simul_powertest_poisson_boxeffect_",
      nb_simul,"nbsimul_",nb_per_SA,
      "nbsimulperSA.pdf")
# cowplot::save_plot(file =here::here("figures",name_plot ),
#                   power_poisson_box, base_height = 20/cm(1), base_width = 14/cm(1), dpi = 1200)

```




# SIMUL WITH REAL UNBALANCED DESIGN
## Dataset
```{r } 
#unbalanced dataset
data_PERF <- read.table(file=here::here("data", "DATACOMPLET_PERF.csv"), sep=",", header=TRUE)
data_PERF$Original_environment<-as.factor(data_PERF$Original_environment)
data_PERF <- data_PERF[data_PERF$Original_environment!="WT3",]
data_PERF <- data_PERF[data_PERF$Test_environment!="GF",]
data_PERF <- data_PERF[data_PERF$Test_environment!="Grape",] #mvrnom doesn't work with unbalanced matrix
data_PERF <- droplevels(data_PERF)
tapply(data_PERF$Population, list(data_PERF$Generation, data_PERF$Population), length)
```



## Normal distribution
```{r } 
####################################
###### Simulation
####################################
#Simul data 
sim <-  sapply(1:nb_simul, simul_fitnessdata_unbalanced, distrib = "normal", 
               unbalanced_dataset = data_PERF, 
               sdpop = 0.5, sdfruithab = 0.5, sdfruithab_ng = 0.5, 
              rho = -0.05, rho_ng = -0.05, 
              sigma = 0.5)
             

sim <- as.data.frame(t(sim))
sim <- add_indic_sign(sim)
sim <- add_sim_number_SA(sim)

####################################
###### Plot genetic
####################################
#Number of simuls for each SA value
tapply(sim$index_SA_Gen, sim$SA_Gen, length)

#Save the same number of simuls for each SA value
nb_per_SA = 50
sim_select_genetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_genet = sort(unique(sim_select_genetic$SA_Gen)), 
                 prop_val_sign = tapply(sim_select_genetic$IndicGen, 
                                        sim_select_genetic$SA_Gen, mean), 
                 prop_val_sign_aov = tapply(sim_select_genetic$IndicGen_aov, 
                                        sim_select_genetic$SA_Gen, mean))


#Plot
plot_genetic_normal_unbalanced_real<-ggplot2::ggplot(data = data_prop, 
                                                     aes(x=val_SA_genet)) + 
   geom_point(aes(y=prop_val_sign, color="LMER"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign, color="LMER"), size = 1, linetype = "dotted") + 
   geom_point(aes(y=prop_val_sign_aov, color="Anova"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign_aov, color="Anova"), size = 1, linetype = "dotted") + 
   ylab("Proportion of simulations with\nsignificant genetic local adaption")  +
   xlab("Intensity of genetic local adaptation (SA)")  +
   ggtitle("Normal data (unbalanced experimental design)") +
   theme_LO_sober +
   labs(color = "Methods", linetype = "Design") +
   scale_color_manual(values = colors) +
   scale_linetype_manual(values = lines)
plot_genetic_normal_unbalanced_real




################################# 
### Plot non-genetic
#################################
#Number of simuls for each SA non-genetic value
tapply(sim$index_SA_NonGen, sim$SA_NonGen, length)

#Save the same number of simuls for each SA value
nb_per_SA 
sim_select_nongenetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "non-genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_nongenet = sort(unique(sim_select_nongenetic$SA_NonGen)), 
                 prop_val_sign = tapply(sim_select_nongenetic$IndicNonGen, 
                                        sim_select_nongenetic$SA_NonGen, mean), 
                 prop_val_sign_aov = tapply(sim_select_nongenetic$IndicNonGen_aov, 
                                        sim_select_nongenetic$SA_NonGen, mean))


#Plot
plot_nongenetic_normal_unbalanced_real<-ggplot2::ggplot(data = data_prop, 
                                                   aes(x=val_SA_nongenet)) + 
   geom_point(aes(y=prop_val_sign, color="LMER"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign, color="LMER"), size = 1, linetype = "dotted") + 
   geom_point(aes(y=prop_val_sign_aov, color="Anova"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign_aov, color="Anova"), size = 1, linetype = "dotted") + 
   ylab("Proportion of simulations with\nsignificant non-genetic local adaption")  +
   xlab("Intensity of non-genetic local adaptation (SA)")  +
   theme_LO_sober + 
   ggtitle("Normal data (unbalanced experimental design)") +
   labs(color = "Methods") +
   scale_color_manual(values = colors)
plot_nongenetic_normal_unbalanced_real





```




## Poisson distribution
```{r } 
####################################
###### Simulation
####################################
#Simul data 
#nb_simul <- 1000
sim <- sapply(1:nb_simul, simul_fitnessdata_unbalanced, distrib = "poisson", 
              unbalanced_dataset = data_PERF, sdpop = 0.5, 
              sdfruithab = 1, sdfruithab_ng = 1, rho = -0.05, rho_ng = -0.05, sigma = 0.5)
sim <- as.data.frame(t(sim))
sim <- add_indic_sign(sim)
sim <- add_sim_number_SA(sim)

####################################
###### Plot genetic
####################################
#Number of simuls for each SA value
tapply(sim$index_SA_Gen, sim$SA_Gen, length)

#Save the same number of simuls for each SA value
# nb_per_SA=10
sim_select_genetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_genet = sort(unique(sim_select_genetic$SA_Gen)), 
                 prop_val_sign = tapply(sim_select_genetic$IndicGen, 
                                        sim_select_genetic$SA_Gen, mean), 
                 prop_val_sign_aov = tapply(sim_select_genetic$IndicGen_aov, 
                                        sim_select_genetic$SA_Gen, mean))


#Plot
plot_genetic_poisson_unbalanced_real<-ggplot2::ggplot(data = data_prop, 
                                                      aes(x=val_SA_genet)) + 
   geom_point(aes(y=prop_val_sign, color="LMER"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign, color="LMER"), size = 1, linetype = "dotted") + 
   geom_point(aes(y=prop_val_sign_aov, color="Anova"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign_aov, color="Anova"), size = 1, linetype = "dotted") + 
   ylab("Proportion of simulations with\nsignificant genetic local adaption")  +
   xlab("Intensity of genetic local adaptation (SA)")  +
   ggtitle("Poisson data (unbalanced experimental design)") +
   theme_LO_sober  + 
   labs(color = "Methods") +
   scale_color_manual(values = colors)
plot_genetic_poisson_unbalanced_real





################################# 
### Plot non-genetic
#################################
#Number of simuls for each SA non-genetic value
tapply(sim$index_SA_NonGen, sim$SA_NonGen, length)

#Save the same number of simuls for each SA value
nb_per_SA 
sim_select_nongenetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "non-genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_nongenet = sort(unique(sim_select_nongenetic$SA_NonGen)), 
                 prop_val_sign = tapply(sim_select_nongenetic$IndicNonGen, 
                                        sim_select_nongenetic$SA_NonGen, mean), 
                 prop_val_sign_aov = tapply(sim_select_nongenetic$IndicNonGen_aov, 
                                        sim_select_nongenetic$SA_NonGen, mean))


colors<-c("LMER" = "#DCA237", "Anova" = "#459B76")
#Plot
plot_nongenetic_poisson_unbalanced_real<-ggplot2::ggplot(data = data_prop, 
                                                   aes(x=val_SA_nongenet)) + 
   geom_point(aes(y=prop_val_sign, color="LMER"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign, color="LMER"), size = 1, linetype = "dotted") + 
   geom_point(aes(y=prop_val_sign_aov, color="Anova"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign_aov, color="Anova"), size = 1, linetype = "dotted") + 
   ylab("Proportion of simulations with\nsignificant non-genetic local adaption")  +
   xlab("Intensity of non-genetic local adaptation (SA)")  +
   theme_LO_sober + 
   ggtitle("Poisson data (unbalanced experimental design)") +
   labs(color = "Methods") +
   scale_color_manual(values = colors)
plot_nongenetic_poisson_unbalanced_real




```






## Binomial distribution
```{r } 
####################################
###### Simulation
####################################
#Simul data 
#nb_simul <- 1000
sim <- sapply(1:nb_simul, simul_fitnessdata_unbalanced, distrib = "binomial", 
              unbalanced_dataset = data_PERF, sdpop = 0.5, 
              sdfruithab = 0.5, sdfruithab_ng = 0.5, 
              rho = -0.05, rho_ng = -0.05, sigma = 0.5)
sim <- as.data.frame(t(sim))
sim <- add_indic_sign(sim)
sim <- add_sim_number_SA(sim)

####################################
###### Plot genetic
####################################
#Number of simuls for each SA value
tapply(sim$index_SA_Gen, sim$SA_Gen, length)

#Save the same number of simuls for each SA value
# nb_per_SA=10
sim_select_genetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_genet = sort(unique(sim_select_genetic$SA_Gen)), 
                 prop_val_sign = tapply(sim_select_genetic$IndicGen, 
                                        sim_select_genetic$SA_Gen, mean), 
                 prop_val_sign_aov = tapply(sim_select_genetic$IndicGen_aov, 
                                        sim_select_genetic$SA_Gen, mean))


#Plot
plot_genetic_Binomial_unbalanced_real<-ggplot2::ggplot(data = data_prop, 
                                                  aes(x=val_SA_genet)) + 
   geom_point(aes(y=prop_val_sign, color="LMER"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign, color="LMER"), size = 1, linetype = "dotted") + 
   geom_point(aes(y=prop_val_sign_aov, color="Anova"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign_aov, color="Anova"), size = 1, linetype = "dotted") + 
   ylab("Proportion of simulations with\nsignificant genetic local adaption")  +
   xlab("Intensity of genetic local adaptation (SA)")  +
   ggtitle("Binomial data (unbalanced experimental design)") +
   theme_LO_sober  + 
   labs(color = "Methods") +
   scale_color_manual(values = colors) 
plot_genetic_Binomial_unbalanced_real



################################# 
### Plot non-genetic
#################################
#Number of simuls for each SA non-genetic value
tapply(sim$index_SA_NonGen, sim$SA_NonGen, length)

#Save the same number of simuls for each SA value
nb_per_SA 
sim_select_nongenetic <- select_sample_simul(dataset_sim = sim, 
                                          type_SA = "non-genetic",
                                          nb_simul_per_SA = nb_per_SA, 
                                          minimum_SA = "0")

#Compute proportion of significant simul for each SA values
data_prop <- data.frame(val_SA_nongenet = sort(unique(sim_select_nongenetic$SA_NonGen)), 
                 prop_val_sign = tapply(sim_select_nongenetic$IndicNonGen, 
                                        sim_select_nongenetic$SA_NonGen, mean), 
                 prop_val_sign_aov = tapply(sim_select_nongenetic$IndicNonGen_aov, 
                                        sim_select_nongenetic$SA_NonGen, mean))


colors<-c("LMER" = "#DCA237", "Anova" = "#459B76")
#Plot
plot_nongenetic_Binomial_unbalanced_real<-ggplot2::ggplot(data = data_prop, 
                                                   aes(x=val_SA_nongenet)) + 
   geom_point(aes(y=prop_val_sign, color="LMER"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign, color="LMER"), size = 1, linetype = "dotted") + 
   geom_point(aes(y=prop_val_sign_aov, color="Anova"), size = 2.5) + 
   geom_line(aes(y=prop_val_sign_aov, color="Anova"), size = 1, linetype = "dotted") + 
   ylab("Proportion of simulations with\nsignificant non-genetic local adaption")  +
   xlab("Intensity of non-genetic local adaptation (SA)")  +
   theme_LO_sober + 
   ggtitle("Binomial data (unbalanced experimental design)") +
   labs(color = "Methods") +
   scale_color_manual(values = colors)
plot_nongenetic_Binomial_unbalanced_real



```



## All plots unbalanced
```{r } 
power_plot_all_unbalanced_real<-cowplot::plot_grid(plot_nongenetic_normal_unbalanced_real,
                                   plot_nongenetic_poisson_unbalanced_real,
                                   plot_nongenetic_Binomial_unbalanced_real,
                                   plot_genetic_normal_unbalanced_real,
                                   plot_genetic_poisson_unbalanced_real,
                                   plot_genetic_Binomial_unbalanced_real,
                          #labels=c("A", "B"), 
                          #label_size = 15,
                          ncol =3, nrow = 2,
                     #    hjust = 0, vjust = 1,
                          scale = c(1,  1))
power_plot_all_unbalanced_real



#Save plot
name_plot<-paste0("Simul_powertest_ALLDATA_UNBALANCED_real",
      nb_simul,"nbsimul_",nb_per_SA,
      "nbsimulperSA.pdf")
# cowplot::save_plot(file =here::here("figures",name_plot ),
#                   power_plot_all_unbalanced_real, base_height = 20/cm(1),
#                   base_width = 42/cm(1), dpi = 1200)
# 

```



